### 2014-10-28 SysCon_article/article_syscon.tex
adding the new folder sysconArticle which contains the paper for Syscon Conference

\documentclass[conference]{IEEEtran}
%
%% article_syscon.tex
%% V1.4
%% 2012/12/27
%% by Smail Rahmoun

%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\usepackage{cite}

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
\usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
\usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}

% *** ALIGNMENT PACKAGES ***
%
\usepackage{array}

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
%\usepackage{stfloats}
\usepackage{dblfloatfix}

% *** PDF, URL AND HYPERLINK PACKAGES ***
\usepackage{url}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{Using NSGA-II to compose model transformations alternatives }

\author{\IEEEauthorblockN{Smail Rahmoun}
\IEEEauthorblockA{Institute for Technological Research\\SystemX\\
Palaiseau France\\
Email: smail.rahmoun@irt-systemx.fr}
\and
\IEEEauthorblockN{Etienne Borde\\ and Laurent Pautet}
\IEEEauthorblockA{TELECOM Paristech Institut\\
LTCI-UMR 5141\\
Paris, France\\
Email: firstname.name@telecom-paristech.fr}}

\maketitle

\begin{abstract}
The size and complexity of modern systems is rapidly increasing. Meanwhile, the ability to understand and maintain such systems is decreasing almost as fast.
Model Driven Engineering (MDE) promotes the automation of design activities by means of model transformations, enabling to cope with systems complexity. However, the design space produced by the composition of these model transformations is difficult to explore automatically. The main reasons that make this exploration difficult are (i) the size of the design space; and (ii) the difficulty to prune inconsistent model transformations compositions.
This paper presents a MDA approach for design space exploration to deal with the ever-growing challenge of designing complex embedded systems. This approach allows the system architects to automatically select the most adequate model transformations compositions by using multi-objectives optimization evolutionary algorithms (MOEA) mechanisms.

%modeling solution for their application, platform, and mapping between application and platform, in an integrated and simultaneous way and at a very early design stage, before system synthesis and code generation have been performed.

%multi-objective optimization evolutionary algorithms which is known to be an important tool for design decision making support.

%The design of safety-critical systems becomes one of the most interesting challenges in modern systems engineering. It requires system architects to address a large number of non-functional properties related to performance, reliability, availability and temporal performance. Moreover, these non-functional properties often conflict with each other, for instance, improving system performance often needs more powerful hardware components, which increases the production cost and power consumption in the meantime.

%and model transformation strategies to identify a sufficient set of design alternatives. This approach will reduce development costs and improve the quality of the final system, because an automated and systematic search will identify more and better design alternatives.

%In this paper, we propose an approach which can analyse a given system architecture, propose design alternatives to it by using model transformations, and do architecture optimization by using some evolutionary algorithms to improve its non-functional properties in an automatic way.
\end{abstract}

%This paper proposes to use multi-objective optimization evolutionary algorithms and model transformation strategies to identify a sufficient set of design alternatives. This approach will reduce development costs and improve the quality of the final system, because an automated and systematic search will identify more and better design alternatives.

% no keywords

\IEEEpeerreviewmaketitle

\section{Introduction}
Nowadays, modern systems become more and more large and complex and therefore more difficult to develop and maintain. For example, embedded critical systems which are often built to accomplish specific functionalities, can integrate thousands of buses, software and hardware components. To guarantee properties such as safety, availability and robustness makes the design of these systems very challenging and complicated.

Model Driven Engineering (MDE) proposes the use of models as the key assets in the development of such systems, and hence all sorts of model modifications are needed. In this way, model transformations become one of the basic building blocks of MDE. Even though MDE is being successfully applied in many scenarios, it still needs appropriate mechanisms to handle the development of complex, large-scale systems. One such mechanism is a facility to make transformations reusable, so that we can apply them to different contexts. In this work, we use generic model transformation to model non-functional properties (NFP) of a system. This process will help us to predict NFP of a system before it development\cite{1291833}. This prediction can be exploited to drive decisions about which components should be used and how they should be connected so as to meet the NFP imposed on the design.

Moreover, an issue in modeling the NFP of a system is that, the NFP could conflict with each other. For example, improving the availability of a service is often done by replication of the service, which causes the decreasing of the response time of these services\cite{Yu:2001:CLA:502059.502038}. Developing a system that satisfies all its NFP simultaneously is often not possible : improving a NFP of a system can deteriorate another NFP. As a consequence, system architects have to come up with several design alternatives and select the optimal solution (Pareto optimal solutions) from all feasible alternatives through the trade-off analysis regarding all NFP\cite{Coello98acomprehensive}.
In order to obtain the set of Pareto optimal alternatives, some advanced multi-objective optimization evolutionary algorithms (MOEA) have been proposed. These algorithm apply some fitness evaluations and generic operators of variation. Thus, they are applicable to search spaces (e.g. design space) taking into account domain specific characteristics of the problem (e.g. prediction of NFP). MOEA also provide selection operators which guide the search towards interesting regions of the search space. As a primary priority, these operators favorise non-dominated solutions : where a solution x1 is dominated by another solution x2 , if x2 matches or exceeds x1 in all objectives. As a secondary priority finding a diverse set of solutions on the Pareto front.

Our approach, consists in improving the NFP of an architecture design through a generic method using model transformations compositions and advanced MOEA. This method will automate the search for optimal compositions from all feasible alternative. More specific, beginning with some initial architecture that specifies a set of NFP, design alternatives are generated by applying model transformation compositions\cite{Jouault:2005:TMA:2153686.2153705}. To get the best design alternatives, the model transformation rules enter into a meta-heuristic loop. That is, we generate transformation rules alternatives (TRA) through some genetic operations such as mutation and crossover. The models transformed by the selected TRA are evaluated and corresponding multiple NFP criteria of interests are obtained afterwards.

The remainder of this paper is organized as follows. Section~\ref{Problem} is dedicated to the problem statement. Section~\ref{Approach} gives an overview  of our approach. While Section~\ref{Adapting} details our approach. Section~\ref{Related} presents the related work. Finally, conclusions and perspectives are given in Section~\ref{Conclu}.
%This paper is organized as follows. In Section~\ref{Problem} we explain the different issues to solve in this paper. Section~\ref{Approach} gives an overview of the idea of using MOEA. In Section~\ref{Adapting}, we illustrate how do we adapt the NSGA-II algorithm to our architecture design problem. Section~\ref{Related} describes related works and discusses in which respect it is different from ours. Finally, conclusions and perspectives are given in Section~\ref{Conclu}.

\section{Problem}
\label{Problem}
During the design of a safety-critical system, it is useful to model non functional objectives (NFP), such as reliability, availability or temporal performances, already in early stages of the development process. Early NFP modeling enables the developer of the system to make design decision based on analyses and simulations. But, one major difficulty is that these NFP can be in conflict with each other, that is, improving one NFP can have a negative impact on others. To construct a system that fulfils all its NFP simultaneously is often not possible. As a consequence, system architects have to consider several design alternatives, and identify a solution that fulfils most NFP (an optimal solution) from all feasible alternatives. A possible solution to this issue is to formalize design alternatives so they can be reusable in different products or projects (i.e. by using model transformation techniques). After the formalization step, explore the design space to identify the set of optimal model transformation alternatives : solutions that fulfils most NFP.

However, with a complex system and a larger design space, it is almost impossible for software architects to find optimal architecture designs. The exploration of such design space can be very difficult to do manually and error-prone. To overcome this issue, we propose an approach to assist architects throughout the modeling phase and automate the design space exploration by using existing multiple objective evolutionary algorithms (MOEA).

Moreover, using MOEA to deal with design alternatives can be challenging. We have (i) to generalize the architecture design problem as a multiple objective optimization problem and, (ii) select the more suitable evolutionary algorithm to solve this optimization problem.

\section{Using evolutionary algorithms for identifying good design alternatives}
\label{Approach}
Figure~\ref{IS} graphically illustrates the approach proposed in this paper by showing the process underlying it. As can be seen in Figure~\ref{IS}, the process starts with an initial input software architecture which could be designed by software architects by using some architecture design language\cite{Medvidovic}. After that, this architecture model is transformed into a set of alternative architecture models (more detailed models) which fulfils a set of NFP such as reliability, availability and response time. To reuse these models into different product, we formalize them by using model transformations and compositions techniques. The final step in Figure~\ref{IS} consists in exploring the design space composed of all model transformation compositions and select which transformation fulfil at best the NFP of the system. This step is done by using an advanced evolutionary algorithm.

\begin{figure}[!t]
\centering
\includegraphics[width=3.49in]{IDMT.pdf}
\caption{Overview of the identification step}
\label{IS}
\end{figure}

\subsection{System architecture modelisation}
Since our application domain is embedded systems, we have chosen AADL (Architecture Analysis \& Design Language) as the underlying architecture description language. AADL has been designed on the foundation of the architecture description language MetaH and its goals are (i) specification of support model-based quality analysis (e.g. safety); and (ii) specification of design architectures for complex embedded systems. It offers a standardized semantics, mostly expressed using natural language and the components are composed hierarchically according to standardized composition rules. AADL also allows the designers to expand model by defining new property sets in their own specific way.

\subsection{Multi-Objective Genetic Algorithm}
In order to deal with the multi-objective nature of our problem (which model transformation achieve the best possible trade-off among NFP) we use MOEA. 
Among the many MOEAs that have been proposed in the literature : NSGA-II\cite{Deb:2002:FEM:2221359.2221582}, SPEA2\cite{Zitzler01spea2:improving}, IBEA\cite{Zitzler04indicatorbasedselection}, only one have been considered in this work, namely NSGA-II (Non-dominated Sorting Genetic Algorithm). It was proposed in the early 90's and still considered today as one of the state-of-the-art MOEA for its robustness across a variety of application domain.

\subsection{NSGA-II}
NSGA-II is an improved version of NSGA\cite{Srinivas94multiobjectiveoptimization} (Non-dominated sorting genetic algorithm). It inherited the non-dominance concept from its old version and showed three innovations, (i) a crowding approach for diversity preservation; (ii) an elitism operator that helps in significantly speeding up the performance of the genetic algorithm (fast non-dominated sort); and (iii) an objective-wise distance computation.

\begin{figure}[!t]
\centering
\includegraphics[width=3.49in]{NSGAII.pdf}
\caption{Schema of the NSGA-II algorithm}
\label{nsgaii}
\end{figure}

Figure~\ref{nsgaii} gives an overview of how to use NSGA-II to automate the exploration of some design space. The steps of this algorithm are as follow :

\begin{enumerate}
\item Initially, Create a random parent population $P_{0}$ composed of N genomes (N = 3 in Figure~\ref{nsgaii}).
\item After that sort this population based on a non domination criterion (e.g. reliability, availability and response time).
\item For each non-dominated solution, assign a fitness (rank) equal to its non-domination level (1 is the best level, 2 is the next best level, and so on).
\item Create a child population $Q_{0}$ of size N using binary tournament selection, recombination, and mutation operators.
\item From the first generation onwards, creation of each new generation constitutes the following steps :
	\begin{enumerate}	
	\item Create the mating pool $R_{t}$ of size 2N by combining the parent population $P_{t}$ and the child population $Q_{t}$.
	\item Sort the combined population $R_{t}$ according to the fast non-dominated sorting procedure to identify all non-dominated fronts $(F_{1} ,F_{2},...,F_{k})$.
	\item Generate the new parent population $P_{t}+1$ of size N by adding non-dominated solutions starting from the first ranked non-dominated front $F1$ and proceeding with the subsequently ranked non-dominated fronts $F_{1} ,F_{2}, . . . ,F_{k}$, till the size exceeds N (Figure~\ref{nsgaii}). This means that the total count of the non-dominated solutions from the fronts $F_{1} ,F_{2}, . . . ,F_{k}$, exceeds the population size N. Now, in order to make the total count of the non-dominated solutions equal to N, it is required to \textbf{reject} some of the lower ranked non-dominated solutions from the last $Fkth$ front. This is achieved through a sorting process based on the crowding distance assigned to each solution contained in the $F_{k}th$ non-dominated front. Thus, the new parent population $P_{t}+1$ of size N is constructed.
	\item Perform the selection, crossover and mutation operations on the newly generated parent population $(P_{t}+1)$ to create the new child population $(Q_{t}+1)$) of size N (Figure~\ref{nsgaii}).
	\end{enumerate}
\item Repeat Step 5 until a stopping criterion is met (e.g. maximum number of generations is reached).

\end{enumerate}

%The solution we propose is to use the NSGA-II algorithm to search efficiently optimal architectures (which fulfil at best the NFP of the system) from the design space. The design space is formalized by using model transformations and the exploration in this space is done by the NSGA-II algorithm

%transformation rules alternatives (TRA). Where 
%Figure~\ref{EAA} gives an overview of how to use NSGA-II to optimize the result of the identification step. The optimization select from the output which alternative apply to satisfy at best the NFP. As we can seen if Figure~\ref{EAA}, The evolution usually starts from a population (parent) of randomly generated individuals, and is an iterative process, with the population in each iteration called a generation.

%In each generation we (i) evaluate the fitness of every individuals, (ii) select the more fit individuals, (iii) create an offspring population and (vi) modify each individuals by using some genetic operators. The algorithm terminates when either a maximum number of generations has been produced, or a satisfactory fitness level has been reached for the population.

%\subsubsection{\textbf{Fitness evaluation}}
%In each generation, the fitness of every individual is evaluated. The fitness is usually the value of the objective function in the optimization problem being solved. In our approach, the fitness $f_{i}(x)$ evaluates a specific NFP of the architecture, for example, $f_{1}$ the reliability, $f_{2}$ the availability and $f_{3}$ the response time. For example TRA11 = {1,2,2} : this transformation rule has the value 1 for the reliability, 2 for the availability and 2 for the response time.
%A fitness function is a particular type of objective function that is used to summarise, as a single figure of merit, how close a given design solution is to achieving the set aims.

%\subsubsection{\textbf{Selection}}
%The selection step determines, which individuals are chosen for mating (recombination) and how many offspring each selected individual produces. Individuals are selected according to their fitness by means of one of the following algorithms : roulette-wheel selection, stochastic universal sampling, local selection, truncation selection or tournament selection. For example in Figure~\ref{EAA}, we select as individuals the transformation rules alternatives TRA11 and TRA12 since they have better fitness than others, TRA11 = {1,2,2} and TRA12 = {1,1,2}.

%\subsubsection{\textbf{Offspring creation}}
%This step consists in producing an offspring population (new individuals) by combining the current population, this process is called mating population. Depending on the representation of the variables of the individuals the following algorithms can be applied : Binary valued recombination, Real valued recombination or discrete recombination. From TRA11 and TRA12 we produce the set \{TRA11, TRA112, TRA121, TRA12\}.

%\subsubsection{\textbf{Genetic operators}}
%After the offspring creation, every individuals of this population undergoes mutation. Offspring variables are mutated by small perturbations (size of the mutation step), with low probability. In Figure~\ref{EAA} we mutate the population \{TRA11, TRA112, TRA121, TRA12\} into \{TRA111, TRA222, TRA221, TRA122\} by using a mutation operator.

%The fitness of the offspring is then computed. The offspring are inserted into the population replacing the parents, producing a new generation. This cycle is performed until the optimization criteria are reached. In this paper we propose to adapt the genetic algorithm NSGA-II to solve the optimization quality problem. This step will be detailed in the next section.

%The more fit individuals are stochastically selected from the current population, and each pair $<$Elements, Rule$>$ is modified (recombined and possibly randomly mutated) to form a new generation. The new generation of candidate solutions is then used in the next iteration of the algorithm. Commonly, the algorithm terminates when either a maximum number of generations has been produced, or a satisfactory fitness level has been reached for the population. In this paper we propose to adapt the genetic algorithm NSGA-II to solve the optimization quality problem. This step will be detailed in the next section.

%To deal with multi-objective optimization problems a generic algorithm has to be adapted in the following ways. Firstly, the ranking of individuals in step 2 and 5 must include all objectives. One simple, but limited, approach is to use a weighted sum of the objective functions, where the weights represent customer preferences. Another approach uses the concept of dominating solutions, where a solution x1 is dominated by another solution x2 , if x2 matches or exceeds x1 in all objectives. Based on this concept, an integer value representing the number of dominating solutions can be assigned to each individual and the individuals with the lowest number are ranked best. Other ranking approaches can be found in the literature [9]. Secondly, diverse individuals should be selected for the next iteration in step 5, since we are interested in a broad set of solutions. This will result in a better chance to find a large set of Pareto-optimal solutions and help to avoid local optima.

%in using multiple-objective genetic algorithms to optimize the result of the identification step and select from the output SOT which rules apply on which elements to satisfy at best the architectural requirements. So we see the architecture design problem as a multiple-objective optimization problem : $x$ represent the solution space which describes all possible architecture specifications that fulfil the requirements of the system : a discrete, combinatorial search space. In figure~\ref{MOEA_approach} $x$ represents the output of the identification step SOT. The non functional objectives to fulfil are : $f_{1}$ reliability, $f_{2}$ availability and $f_{3}$ response time. The conditions based on $g_{j}(x)$ and $h_{j}(x)$ with $j = 1, 2, ...K$ represents a number of constraints which any feasible solution must satisfy.

%There exists m = 3 objectives : $f_{1}$ reliability, $f_{2}$ availability and $f_{3}$ response time. The conditions based on $g_{j}(x)$ and $h_{j}(x) with j=1,2,...K$ represents a number of constraints which any feasible solution must satisfy. The aim is not to provide one optimal solution but rather to provide a large variety of non-dominated solutions, which represent trade-off in the objective space. The dominance relation is represented like follow :\\ 
%a solution $x$ dominates a solution $x'$ is equivalent to $ \forall i \in {1,..,M} : f_{i}(x) \leq f_{i}(x')$ and \\
%$ \exists j \in {1,..,M} : f_{j}(x) < f_{i}(x')$
%Evolutionary algorithms are preferred for solving multi-objective optimization problems. These evolutionary algorithms follow the idea of natural evolution and try to optimize or improve a population of candidate solutions,

\section{Compose model transformation alternatives by using NSGA-II}
\label{Adapting}

In this paper we propose a generic method to automate the search of optimal architectures (which fulfil at best the NFP of the system) from the design space. To represent the design space (set of architecture alternatives) we use model transformations compositions. The exploration step is done by using the NSGA-II algorithm.

\subsection{Genome representation}
The first step of our work consists in applying the definition of the multi-objective optimization problem on our architecture design problem. Where the population to optimize or the design space represent a set of architecture alternatives and the objectives functions are $f_{1}:$ reliability, $f_{2}:$ availability and $f_{3}:$ response time. The architecture alternatives are formalized in a way that allow their reuse in different projects or products. To do so, we use model transformations methods. An issue in using such methods is their complexity : how to identify which elements of the input architecture model transformation alternatives can be applied. To ease the development and maintenance of such model transformations, we propose to use a rule-based transformation language and composition mechanisms. These languages define rules which define the mapping from source elements (elements of the software architecture) to target element (architecture alternative).

In our approach we call these rules TRA (Transformation Rules Alternatives). They represent the genomes to optimize in our multi-objective problem. Figure~\ref{genome} gives an overview of these genomes. Each genome $G_{i}, i \in {1,2,...,n}$ is composed of a set of TRA $(G = {TRA_{i}, i \in {1,2,...n}})$. Each $TRA_{i}$ is, in turn, encoded as a pair $TRA_{i} = <Elements_{i},Rule_{i}>$ where $Elements_{i} (i ={1,2,...,n})$ is a list of elements from the input model, and $Rule_{i} (i ={1,2,...,n})$ is a transformation rule which can be applied to $Elements_{i}$.

\begin{figure}[!t]
\centering
\includegraphics[width=3.49in]{genome.pdf}
\caption{Genome overview}
\label{genome}
\end{figure}

\subsection{Genome evaluation}
In each generation, the fitness of every genome in the population is evaluated. The fitness is usually the value of the objective function in the optimization problem being solved. We defined in our work one fitness function corresponding to three objectives reliability, availability and response time.
The aim of our work is to maximize these three objectives.

The more fit genomes are stochastically selected from the current population, and each genome is modified (recombined and possibly randomly mutated) to form a new generation.

%\subsection{Adapting NSGA-II To explore the design space}
%The second step of our approach consists in (i) the exploration of the design space (composed of the set of genomes described above); and (ii) selection of the optimal genomes. This step is realised by adapting the concepts of the NSGA-II algorithm to our design problem. To do so, we use the same algorithm as described previously. Except that each genome is represented by a set of TRA.

\subsection{Genetic operators definition}
In NSGA-II, in each iteration, the N genomes selected from the previous generation are used to create new N genomes using genetic operators. This improves the existing solutions by mixing their genetic material (crossover) and/or by creating new material (mutation). Before applying the operators, the solutions are selected according to their fitness values, see Figure~\ref{nsgaii}. In our work, binary tournament selection, crossover and mutation operators are used.

\subsubsection{\textbf{Binary tournament selection}}
This operation consists of choosing some genomes at random in the population, and selecting the fittest two for reproduction. The selection criteria are the rank of the containing front and the crowding distance for solutions within the same front. Several tournaments are run to produce the N needed genomes.

Figure~\ref{binary} illustrates this operation. We have four genomes (G1,G2,G3,G4) and we apply two tournaments to produce the needed genomes. The final genomes of the competition will always be the fittest genomes in the population. The more successful the genome is in competition, the more often that genome is expected to appear in the mating pool (In Figure~\ref{binary} the fittest genome is G4).

\begin{figure}[!t]
\centering
\includegraphics[width=3.49in]{bt.pdf}
\caption{Tournament Competition between Genomes}
\label{binary}
\end{figure}

\subsubsection{\textbf{Crossover}}
The crossover consists of producing new genomes from the existing ones. When two genomes are selected using the binary tournament selection, two offspring solutions are created, with a given crossover probability, by exchanging parts of the parent genomes. This consists in randomly selecting a cut point in the genome vector, and all the target fragments beyond that point in either parent are swapped between the two parents.

Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes G1 and G2 respectively composed of \{TRA11,TRA12,TRA13\} and \{TRA21,TRA22,TRA23\} to produce a new genome G3. As can be seen in Figure~\ref{crossover}, this operator combines G1 and G2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.

\begin{figure}[!t]
\centering
\includegraphics[width=3.49in]{crossover.pdf}
\caption{Crossover operator}
\label{crossover}
\end{figure}

\subsubsection{\textbf{Mutation}}
After performing the crossover, the obtained solutions could be mutated with a given mutation probability.
The mutation operator act on a single genome G1 to obtained a muted genome G11 as follows. The mutation operator selects a gene at random in the genome and changes its value. In Figure~\ref{mutation}, the third tile TRA13 is selected to mutate into TRA14 : we apply a different rule (i.e. rule4) to the set of selected elements.

%In the genetic algorithm used in the evolutionary design system above the genotypes consist of 1's and 0's, applying the mutation operator to a genotype of this kind switches a randomly selected 1 to a 0 or vice versa. 
%Indicating the core in the tile TRA as cs and ct as the core with which cs communicates most frequently, cs is remapped on a tile adjacent to Ts so as to reduce the distance between cs and ct . thus obtaining the mutated chromosome C0.

\begin{figure}[!t]
\centering
\includegraphics[width=3.49in]{mutation.pdf}
\caption{Mutation operator}
\label{mutation}
\end{figure}

%\subsection{\textbf{Use case}}
%Figure~\ref{nsgaDesign} gives an overview of the application of

%\begin{figure}[!t]
%\centering
%\includegraphics[width=3.49in]{nsgaDesign.pdf}
%\caption{Overview of the adaptation of NSGA-II}
%\label{nsgaDesign}
%\end{figure}

\section{Related Work}
\label{Related}
There is some existing works related to our contribution and they are different from our proposed approach. First, Grunske\cite{Gr5069138} framework called ArchOpteryx which use also evolutionary algorithms to deal with design alternatives selection. Unlike this method, our approach consider dependencies between model alternatives. There is also the DesignBots\cite{Diaz-Pace:2007:UPT:1784860.1784865}, where each transformation is not performed atomically unlike our approach. There is also the cyclic process\cite{Bosch99softwarearchitecture} to deal with the optimization of non-functional properties. The benefit of this process is its simplicity. The process can be tailored to different non-functional properties by using specific evaluation methods and architecture transformations. But this process focuses on only one non-functional property at a time unlike us who take into account several properties at a same time (e.g. reliability, availability and response time).

\section{Conclusion}
\label{Conclu}
An architecture design method has been presented that explicitly addresses the NFP put on the architecture. The proposed approach aims at improving system architecture models using two mechanisms. In one side model transformations compositions to ensure model design alternatives, which represent the design space. In the other side an elitist multiple-objective optimisation algorithm to explore this design space.

The main benefits of this approach is to handle a large search spaces of quality optimization problems and to automate the identification of good architecture design alternatives. This will reduce development costs and improve the quality of the final system. Additionally this approach enables the ranking of design alternatives with respect to conflicting NFP and the possibility to reuse these alternatives in other projects or products by using model transformations.
In the future, we plan to integrate our approach in an existing framework RAMSES\footnote{Refinement of AADL Models for the Synthesis of Embdded Systems. \url{http://penelope.enst.fr/aadl/wiki/Projects}} which apply selection of design alternatives. Also evaluate our approach in more details quantitatively (i.e. experimenting it on a an industrial case study).

%Older works and experiments have shown that evolutionary algorithms and multiobjective optimization strategies can be used to identify Pareto-optimal or near Pareto-optimal architecture designs, which can be used as an input for architecture trade-off analysis techniques.

%The main benefit of this approach is the ability to handle the large search spaces of quality optimization problems and to automate the identification of good architecture design alternatives. This will reduce development costs and improve the quality of the final system. Addition- ally this approach enables the ranking of design decisions (architectural refactorings) with respect to conflicting quality requirements.

\section{Acknowledgment}
This research work has been carried out under the leadership of the Technological Research Institute SystemX, and therefore granted with public funds within the scope of the French Program "Investissements d’Avenir".

\begin{thebibliography}{1}

\bibitem{Gr5069138}
A.~Aleti, S.~Bjornander, L.~Grunske, and I.~Meedeniya, ``Archeopterix: An
  extendable tool for architecture optimization of aadl models,'' in
  \emph{Model-Based Methodologies for Pervasive and Embedded Software, 2009.
  MOMPES '09. ICSE Workshop on}, May 2009, pp. 61--71.

\bibitem{1291833}
S.~Balsamo, A.~di~Marco, P.~Inverardi, and M.~Simeoni, ``Model-based
  performance prediction in software development: a survey,'' \emph{Software
  Engineering, IEEE Transactions on}, vol.~30, no.~5, pp. 295--310, May 2004.

\bibitem{Bosch99softwarearchitecture}
J.~Bosch, P.~Molin, J.~Bosch, and P.~Molin, ``Software architecture design:
  Evaluation and transformation,'' in \emph{In 1999 IEEE Engineering of
  Computer Based Systems Symposium. IEEE Computer Based Systems}, 1999, 
  pp. 4--10.

\bibitem{Coello98acomprehensive}
C.~A.~C. Coello, ``A comprehensive survey of evolutionary-based multiobjective
  optimization techniques,'' \emph{Knowledge and Information Systems}, vol.~1,
  pp. 269--308, 1998.

\bibitem{Deb:2002:FEM:2221359.2221582}
K.~Deb, A.~Pratap, S.~Agarwal, and T.~Meyarivan, ``A fast and elitist
  multiobjective genetic algorithm: Nsga-ii,'' \emph{Trans. Evol. Comp},
  vol.~6, no.~2, pp. 182--197, Apr. 2002. [Online]. Available:
  \url{http://dx.doi.org/10.1109/4235.996017}

\bibitem{Deb:2001:MOU:559152}
K.~Deb and D.~Kalyanmoy, \emph{Multi-Objective Optimization Using Evolutionary
  Algorithms}.\hskip 1em plus 0.5em minus 0.4em\relax New York, NY, USA: John
  Wiley \&amp; Sons, Inc., 2001.

\bibitem{Diaz-Pace:2007:UPT:1784860.1784865}
J.~A. D\'{\i}az-Pace and M.~R. Campo, ``Using planning techniques to assist
  quality-driven architectural design exploration,'' in \emph{Proceedings of
  the Quality of Software Architectures 3rd International Conference on
  Software Architectures, Components, and Applications}, ser. QoSA'07.\hskip
  1em plus 0.5em minus 0.4em\relax Berlin, Heidelberg: Springer-Verlag, 2007,
  pp. 33--52. [Online]. Available:
  \url{http://dl.acm.org/citation.cfm?id=1784860.1784865}

\bibitem{Johnsen1753}
A.~Johnsen and K.~Lundqvist, ``Developing dependable software-intensive
  systems: Aadl vs. east-adl,'' in \emph{Ada-Europe 2011}, A.~Romanovsky and
  T.~Vardanega, Eds.\hskip 1em plus 0.5em minus 0.4em\relax Springer-Verlag,
  June 2011, pp. 103--117. [Online]. Available:
  \url{http://www.es.mdh.se/publications/1753-}

\bibitem{Jouault:2005:TMA:2153686.2153705}
F.~Jouault and I.~Kurtev, ``Transforming models with atl,'' in
  \emph{Proceedings of the 2005 International Conference on Satellite Events at
  the MoDELS}, ser. MoDELS'05.\hskip 1em plus 0.5em minus 0.4em\relax Berlin,
  Heidelberg: Springer-Verlag, 2006, pp. 128--138. 
  [Online]. Available:  \url{http://dx.doi.org/10.1007/11663430_14}

\bibitem{Kleppe2003}
A.~G. Kleppe, J.~Warmer, and W.~Bast, \emph{MDA Explained: The Model Driven
  Architecture: Practice and Promise}.\hskip 1em plus 0.5em minus 0.4em\relax
  Boston, MA, USA: Addison-Wesley Longman Publishing Co., Inc., 2003.

\bibitem{Medvidovic}
N.~Medvidovic and R.~N. Taylor, ``A classification and comparison framework for
  software architecture description languages,'' \emph{IEEE Trans. Softw.
  Eng.}, vol.~26, no.~1, pp. 70--93, Jan. 2000. [Online]. Available:
  \url{http://dx.doi.org/10.1109/32.825767}

\bibitem{Srinivas94multiobjectiveoptimization}
N.~Srinivas and K.~Deb, ``Multiobjective optimization using nondominated
  sorting in genetic algorithms,'' \emph{Evolutionary Computation}, vol.~2, 
  pp. 221--248, 1994.

\bibitem{Tisi:conf/ecmdafa/TisiJFCB09}
M.~Tisi, F.~Jouault, P.~Fraternali, S.~Ceri, and J.~B{\'{e}}zivin, ``On the use
  of higher-order model transformations,'' in \emph{Model Driven Architecture -
  Foundations and Applications, 5th European Conference, {ECMDA-FA} 2009,
  Enschede, The Netherlands, June 23-26, 2009. Proceedings}, 2009, pp. 18--33.
  [Online]. Available: \url{http://dx.doi.org/10.1007/978-3-642-02674-4_3}

\bibitem{Yu:2001:CLA:502059.502038}
H.~Yu and A.~Vahdat, ``The costs and limits of availability for replicated
  services,'' \emph{SIGOPS Oper. Syst. Rev.}, vol.~35, no.~5, pp. 29--42, Oct.
  2001. [Online]. Available: 
  \url{http://doi.acm.org/10.1145/502059.502038}

\bibitem{Zitzler01spea2:improving}
E.~Zitzler, M.~Laumanns, and L.~Thiele, ``Spea2: Improving the strength pareto
  evolutionary algorithm,'' Tech. Rep., 2001.

\bibitem{Zitzler04indicatorbasedselection}
E.~Zitzler and S.~Künzli, ``Indicator-based selection in multiobjective
  search,'' in \emph{in Proc. 8th International Conference on Parallel Problem
  Solving from Nature (PPSN VIII}.\hskip 1em plus 0.5em minus 0.4em\relax
  Springer, 2004, pp. 832--842.

\end{thebibliography}

\end{document}

### 2014-10-28 SysCon_article/article_syscon.tex
modification of all the sections of the paper

@@
 However, the design space produced by the composition of these model transformations is difficult to explore automatically.
-The main reasons that make this exploration difficult are (i) the size of the design space; and (ii) the difficulty to prune inconsistent model transformations compositions.
+The main reason that make this exploration difficult is the size of the design space : the number of possible design choices grows exponentially with the number of model transformation alternatives.
 This paper presents a MDA approach for design space exploration to deal with the ever-growing challenge of designing complex embedded systems.
@@
 One such mechanism is a facility to make transformations reusable, so that we can apply them to different contexts.
-In this work, we use generic model transformation to model non-functional properties (NFP) of a system.
+In this work, we use generic model transformation to model design alternatives of the system.
 This process will help us to predict NFP of a system before it development\cite{1291833}.
@@
 
-Moreover, an issue in modeling the NFP of a system is that, the NFP could conflict with each other.
-For example, improving the availability of a service is often done by replication of the service, which causes the decreasing of the response time of these services\cite{Yu:2001:CLA:502059.502038}.
-Developing a system that satisfies all its NFP simultaneously is often not possible : improving a NFP of a system can deteriorate another NFP.
+Moreover, an issue in modeling the NFP of a system is that, the NFP could conflict\footnote{improving one property can have a negative impact on other properties} with each other.
+For example, improving the availability of a service is often done by replication of the service, which causes the increasing of the response time of these services\cite{Yu:2001:CLA:502059.502038}.
+Developing a system that satisfies at best all its NFP simultaneously is often not possible : improving a NFP of a system can deteriorate another NFP.
 As a consequence, system architects have to come up with several design alternatives and select the optimal solution (Pareto optimal solutions) from all feasible alternatives through the trade-off analysis regarding all NFP\cite{Coello98acomprehensive}.
+
 In order to obtain the set of Pareto optimal alternatives, some advanced multi-objective optimization evolutionary algorithms (MOEA) have been proposed.
@@
 prediction of NFP).
-MOEA also provide selection operators which guide the search towards interesting regions of the search space.
-As a primary priority, these operators favorise non-dominated solutions : where a solution x1 is dominated by another solution x2 , if x2 matches or exceeds x1 in all objectives.
-As a secondary priority finding a diverse set of solutions on the Pareto front.
+MOEA also provides selection operators which guide the search towards interesting regions of the search space by (i) favorizing non-dominated solutions : where a solution x1 is dominated by another solution x2 , if x2 matches or exceeds x1 in all objectives; (ii) finding a diverse set of solutions on the Pareto front.
 
 Our approach, consists in improving the NFP of an architecture design through a generic method using model transformations compositions and advanced MOEA.
-This method will automate the search for optimal compositions from all feasible alternative.
+This method will automate the search for optimal compositions from all feasible alternatives.
 More specific, beginning with some initial architecture that specifies a set of NFP, design alternatives are generated by applying model transformation compositions\cite{Jouault:2005:TMA:2153686.2153705}.
-To get the best design alternatives, the model transformation rules enter into a meta-heuristic loop.
+To get the non-dominated alternatives, model transformation rules enter into a meta-heuristic loop.
 That is, we generate transformation rules alternatives (TRA) through some genetic operations such as mutation and crossover.
-The models transformed by the selected TRA are evaluated and corresponding multiple NFP criteria of interests are obtained afterwards.
+The models transformed by the selected TRA are evaluated and corresponding multiple NFP criteria of interests are obtained after application of transformations in order to obtain more precise analysis.
 
-The remainder of this paper is organized as follows.
+The reminder of this paper is organized as follows.
+Section~\ref{Problem} is dedicated to the problem statement.
+Section~\ref{Approach} gives an overview  of our approach.
+While Section~\ref{Adapting} details our approach.
+Section~\ref{Related} presents the related work.
+%The remainder of this paper is organized as follows.
 Section~\ref{Problem} is dedicated to the problem statement.
@@
 Finally, conclusions and perspectives are given in Section~\ref{Conclu}.
-%This paper is organized as follows.
-In Section~\ref{Problem} we explain the different issues to solve in this paper.
-Section~\ref{Approach} gives an overview of the idea of using MOEA.
-In Section~\ref{Adapting}, we illustrate how do we adapt the NSGA-II algorithm to our architecture design problem.
-Section~\ref{Related} describes related works and discusses in which respect it is different from ours.
-Finally, conclusions and perspectives are given in Section~\ref{Conclu}.
 
@@
 \label{Problem}
-During the design of a safety-critical system, it is useful to model non functional objectives (NFP), such as reliability, availability or temporal performances, already in early stages of the development process.
+During the design of a safety-critical system, it is useful to model non functional properties (NFP), such as reliability, availability or temporal performances, already in early stages of the development process.
 Early NFP modeling enables the developer of the system to make design decision based on analyses and simulations.
@@
 As a consequence, system architects have to consider several design alternatives, and identify a solution that fulfils most NFP (an optimal solution) from all feasible alternatives.
-A possible solution to this issue is to formalize design alternatives so they can be reusable in different products or projects (i.e.
+
+A possible solution to this issue is to implement these design alternatives in a way that they can be seen as design patterns.
+Where each pattern implement a well-known architectural solution which fulfils a set of NFP.
+To formalize these design patterns in a way that allow their reuse in different projects or products we implement them as model transformations.
+
+%These design patterns are implemented as model transformations. It  which allows us to applied them to various sets of NFP
+
+%improving a set NFP, and solving the conflict between these NFP.
+Model transformations are usually defined to be generic such as design patterns which allows us to applied them to various sets of NFP.
+
+%A set of model transformations that implement refinements or improvements of the source model, each of them focusing on increasing the satisfaction of a given goal (reducing power consumption, increasing availability, etc.).
+These model transformations can be seen as design patterns, each of them implementing a well-known solution to a given quality objective.
+
+%A possible solution to this issue is to formalize design alternatives so they can be reusable in different products or projects (i.e.
 by using model transformation techniques).
@@
 
-However, with a complex system and a larger design space, it is almost impossible for software architects to find optimal architecture designs.
+The second challenge in this work comes from the size of the design space to explore in order to study such NFP trade-offs.
+With a complex system and a larger design space, it is almost impossible for software architects to find optimal architecture designs.
 The exploration of such design space can be very difficult to do manually and error-prone.
@@
 
-Moreover, using MOEA to deal with design alternatives can be challenging.
-We have (i) to generalize the architecture design problem as a multiple objective optimization problem and, (ii) select the more suitable evolutionary algorithm to solve this optimization problem.
+Moreover, using MOEA to deal with mode transformations alternatives can be challenging.
+We have (i) to generalize the architecture design problem as a multiple objective optimization problem; (ii) select the more suitable evolutionary algorithm to solve this optimization problem; and (iii) adapting the notions of model transformation compositions to this evolutionary algorithm.
 
@@
 As can be seen in Figure~\ref{IS}, the process starts with an initial input software architecture which could be designed by software architects by using some architecture design language\cite{Medvidovic}.
-After that, this architecture model is transformed into a set of alternative architecture models (more detailed models) which fulfils a set of NFP such as reliability, availability and response time.
-To reuse these models into different product, we formalize them by using model transformations and compositions techniques.
+After that, this architecture model is transformed into a set of alternative architecture models (more detailed models) which fulfils a set of competing NFP such as reliability, availability and response time.
+To solve the trade-off between NFP we expressed the architecture alternatives as design patterns implemented by means of model transformations and compositions techniques.
 The final step in Figure~\ref{IS} consists in exploring the design space composed of all model transformation compositions and select which transformation fulfil at best the NFP of the system.
@@
 \subsection{System architecture modelisation}
+%For software architecture modeling step, as a natural extension of previous work RAMSES and  we choose to use AADL (Architecture Analysis & Design Language) as the underlying architecture description language.
+
 Since our application domain is embedded systems, we have chosen AADL (Architecture Analysis \& Design Language) as the underlying architecture description language.
-AADL has been designed on the foundation of the architecture description language MetaH and its goals are (i) specification of support model-based quality analysis (e.g.
-safety); and (ii) specification of design architectures for complex embedded systems.
+AADL has been designed on the foundation of the architecture description language MetaH and its goals are (i) specification of quality analysis (e.g.
+safety); and (ii) design architectures for complex embedded systems.
 It offers a standardized semantics, mostly expressed using natural language and the components are composed hierarchically according to standardized composition rules.
 AADL also allows the designers to expand model by defining new property sets in their own specific way.
+The other reason of choosing AADL is to integrate our work in an existing framework RAMSES\footnote{Refinement of AADL Models for the Synthesis of Embdded Systems.
+\url{http://penelope.enst.fr/aadl/wiki/Projects}} which apply selection of design alternatives.
 
@@
 NSGA-II is an improved version of NSGA\cite{Srinivas94multiobjectiveoptimization} (Non-dominated sorting genetic algorithm).
-It inherited the non-dominance concept from its old version and showed three innovations, (i) a crowding approach for diversity preservation; (ii) an elitism operator that helps in significantly speeding up the performance of the genetic algorithm (fast non-dominated sort); and (iii) an objective-wise distance computation.
+It inherited the non-dominance concept from NSGA and showed three innovations, (i) a crowding approach for diversity preservation; (ii) an elitism operator that helps in significantly speeding up the performance of the genetic algorithm (fast non-dominated sort); and (iii) an objective-wise distance computation.
 
@@
 
-Figure~\ref{nsgaii} gives an overview of how to use NSGA-II to automate the exploration of some design space. The steps of this algorithm are as follow :
+Figure~\ref{nsgaii} gives an overview of how to use NSGA-II to automate the exploration of complex systems design space. The steps of this algorithm are as follow :
 
@@
 \item Initially, Create a random parent population $P_{0}$ composed of N genomes (N = 3 in Figure~\ref{nsgaii}).
-\item After that sort this population based on a non domination criterion (e.g. reliability, availability and response time).
+\item Sort the current population based on a non domination criterion (e.g. reliability, availability and response time).
 \item For each non-dominated solution, assign a fitness (rank) equal to its non-domination level (1 is the best level, 2 is the next best level, and so on).
@@
 
-%The solution we propose is to use the NSGA-II algorithm to search efficiently optimal architectures (which fulfil at best the NFP of the system) from the design space.
-The design space is formalized by using model transformations and the exploration in this space is done by the NSGA-II algorithm
-
-%transformation rules alternatives (TRA). Where 
-%Figure~\ref{EAA} gives an overview of how to use NSGA-II to optimize the result of the identification step.
-The optimization select from the output which alternative apply to satisfy at best the NFP.
-As we can seen if Figure~\ref{EAA}, The evolution usually starts from a population (parent) of randomly generated individuals, and is an iterative process, with the population in each iteration called a generation.
-
-%In each generation we (i) evaluate the fitness of every individuals, (ii) select the more fit individuals, (iii) create an offspring population and (vi) modify each individuals by using some genetic operators.
-The algorithm terminates when either a maximum number of generations has been produced, or a satisfactory fitness level has been reached for the population.
-
-%\subsubsection{\textbf{Fitness evaluation}}
-%In each generation, the fitness of every individual is evaluated.
-The fitness is usually the value of the objective function in the optimization problem being solved.
-In our approach, the fitness $f_{i}(x)$ evaluates a specific NFP of the architecture, for example, $f_{1}$ the reliability, $f_{2}$ the availability and $f_{3}$ the response time.
-For example TRA11 = {1,2,2} : this transformation rule has the value 1 for the reliability, 2 for the availability and 2 for the response time.
-%A fitness function is a particular type of objective function that is used to summarise, as a single figure of merit, how close a given design solution is to achieving the set aims.
-
-%\subsubsection{\textbf{Selection}}
-%The selection step determines, which individuals are chosen for mating (recombination) and how many offspring each selected individual produces.
-Individuals are selected according to their fitness by means of one of the following algorithms : roulette-wheel selection, stochastic universal sampling, local selection, truncation selection or tournament selection.
-For example in Figure~\ref{EAA}, we select as individuals the transformation rules alternatives TRA11 and TRA12 since they have better fitness than others, TRA11 = {1,2,2} and TRA12 = {1,1,2}.
-
-%\subsubsection{\textbf{Offspring creation}}
-%This step consists in producing an offspring population (new individuals) by combining the current population, this process is called mating population.
-Depending on the representation of the variables of the individuals the following algorithms can be applied : Binary valued recombination, Real valued recombination or discrete recombination.
-From TRA11 and TRA12 we produce the set \{TRA11, TRA112, TRA121, TRA12\}.
-
-%\subsubsection{\textbf{Genetic operators}}
-%After the offspring creation, every individuals of this population undergoes mutation.
-Offspring variables are mutated by small perturbations (size of the mutation step), with low probability.
-In Figure~\ref{EAA} we mutate the population \{TRA11, TRA112, TRA121, TRA12\} into \{TRA111, TRA222, TRA221, TRA122\} by using a mutation operator.
-
-%The fitness of the offspring is then computed.
-The offspring are inserted into the population replacing the parents, producing a new generation.
-This cycle is performed until the optimization criteria are reached.
-In this paper we propose to adapt the genetic algorithm NSGA-II to solve the optimization quality problem.
-This step will be detailed in the next section.
-
-%The more fit individuals are stochastically selected from the current population, and each pair $<$Elements, Rule$>$ is modified (recombined and possibly randomly mutated) to form a new generation.
-The new generation of candidate solutions is then used in the next iteration of the algorithm.
-Commonly, the algorithm terminates when either a maximum number of generations has been produced, or a satisfactory fitness level has been reached for the population.
-In this paper we propose to adapt the genetic algorithm NSGA-II to solve the optimization quality problem.
-This step will be detailed in the next section.
-
-%To deal with multi-objective optimization problems a generic algorithm has to be adapted in the following ways.
-Firstly, the ranking of individuals in step 2 and 5 must include all objectives.
-One simple, but limited, approach is to use a weighted sum of the objective functions, where the weights represent customer preferences.
-Another approach uses the concept of dominating solutions, where a solution x1 is dominated by another solution x2 , if x2 matches or exceeds x1 in all objectives.
-Based on this concept, an integer value representing the number of dominating solutions can be assigned to each individual and the individuals with the lowest number are ranked best.
-Other ranking approaches can be found in the literature [9].
-Secondly, diverse individuals should be selected for the next iteration in step 5, since we are interested in a broad set of solutions.
-This will result in a better chance to find a large set of Pareto-optimal solutions and help to avoid local optima.
-
-%in using multiple-objective genetic algorithms to optimize the result of the identification step and select from the output SOT which rules apply on which elements to satisfy at best the architectural requirements.
-So we see the architecture design problem as a multiple-objective optimization problem : $x$ represent the solution space which describes all possible architecture specifications that fulfil the requirements of the system : a discrete, combinatorial search space.
-In figure~\ref{MOEA_approach} $x$ represents the output of the identification step SOT.
-The non functional objectives to fulfil are : $f_{1}$ reliability, $f_{2}$ availability and $f_{3}$ response time.
-The conditions based on $g_{j}(x)$ and $h_{j}(x)$ with $j = 1, 2, ...K$ represents a number of constraints which any feasible solution must satisfy.
-
-%There exists m = 3 objectives : $f_{1}$ reliability, $f_{2}$ availability and $f_{3}$ response time.
-The conditions based on $g_{j}(x)$ and $h_{j}(x) with j=1,2,...K$ represents a number of constraints which any feasible solution must satisfy.
-The aim is not to provide one optimal solution but rather to provide a large variety of non-dominated solutions, which represent trade-off in the objective space.
-The dominance relation is represented like follow :\\
-%a solution $x$ dominates a solution $x'$ is equivalent to $ \forall i \in {1,..,M} : f_{i}(x) \leq f_{i}(x')$ and \\
-%$ \exists j \in {1,..,M} : f_{j}(x) < f_{i}(x')$
-%Evolutionary algorithms are preferred for solving multi-objective optimization problems.
-These evolutionary algorithms follow the idea of natural evolution and try to optimize or improve a population of candidate solutions,
-
 \section{Compose model transformation alternatives by using NSGA-II}
@@
 The exploration step is done by using the NSGA-II algorithm.
+
+\subsection{Model transformations languages}
+In general, model transformations are grouped into two main categories of model transformation languages : (i) rule-based transformation languages, or (ii)
+imperative transformation languages.
+We used in our work the first category of languages since it express model transformation logics in a way that is easy to interpret and \textbf{adapt} in other methods (in this paper MOEA).
+To be continued by giving more explanations about rule-based transformations languages
+
+%Examples of rule-based transformation languages ATL (for Atlas Transformation Language) and QVT-R (for ).
+
+%such as ATL and QVT-R, are of great interest in our context since they express model transformation logics in a way that is easy to interpret and adapt.
+Indeed, modifying the pattern matching part of a transformation rule is sufficient to modify the set of elements this rule applies to.
+In addition, superimposition helps to combine different sets of rules [15].
+Contrasting with rule-based formalisms, the adaptation of imperative transformation languages requires a deep understanding of the control flow graph that leads to the execution of one or another transformation.
+Model transformations we deal with in this paper are endogenous (AADL[13] to AADL model transformations) in order to refine or improve the architecture of an embedded system while representing the result of this refinement in an analyzable model (using AADL as an output language).
 
@@
 Figure~\ref{binary} illustrates this operation.
-We have four genomes (G1,G2,G3,G4) and we apply two tournaments to produce the needed genomes.
+On this figure, we suppose we have four genomes (G1,G2,G3,G4) and we apply two tournaments to produce the needed genomes.
 The final genomes of the competition will always be the fittest genomes in the population.
@@
 After performing the crossover, the obtained solutions could be mutated with a given mutation probability.
-The mutation operator act on a single genome G1 to obtained a muted genome G11 as follows.
+The mutation operator act on a single genome G1 to obtained a muted genome G11 acts as follows.
 The mutation operator selects a gene at random in the genome and changes its value.
@@
 \label{Related}
-There is some existing works related to our contribution and they are different from our proposed approach.
-First, Grunske\cite{Gr5069138} framework called ArchOpteryx which use also evolutionary algorithms to deal with design alternatives selection.
-Unlike this method, our approach consider dependencies between model alternatives.
-There is also the DesignBots\cite{Diaz-Pace:2007:UPT:1784860.1784865}, where each transformation is not performed atomically unlike our approach.
-There is also the cyclic process\cite{Bosch99softwarearchitecture} to deal with the optimization of non-functional properties.
+Our work is based on system performance prediction\cite{1291833} by using model transformations techniques and multi-objective metaheuristic optimization\cite{Coello98acomprehensive}.
+
+Aleti et al.\cite{Gr5069138} have developed the ArchOpteryx framework.
+ArchOpteryx assists the system architects during the design to create architectures that meet non-functional properties by using multi-objective optimization strategies.
+Unlike this method, design alternatives are implemented as model transformations driven by NFP.
+Using model transformations help the design architects to (i) automating the system production; (ii) reusing architecture alternatives in other projects (or products) and (iii) solving the competition issue between NFP.
+Compared to DesignBots\cite{Diaz-Pace:2007:UPT:1784860.1784865}, in our method model transformations are not decomposed into subplans, each transformation is performed atomically.
+
+Koziolek et al.\cite{Koziolek:2011:PAA:2000259.2000267} have developed the Peropteryx framework for improvement of system architecture models using a metaheuristic search guided by architectural tactics.
+
+For the optimization of NFP another work consists at using a cyclic process\cite{Bosch99softwarearchitecture}.
 The benefit of this process is its simplicity.
@@
 The proposed approach aims at improving system architecture models using two mechanisms.
-In one side model transformations compositions to ensure model design alternatives, which represent the design space.
-In the other side an elitist multiple-objective optimisation algorithm to explore this design space.
+On the one hand, model transformations compositions to formalize model design alternatives.
+On the other hand, an elitist multiple-objective optimisation algorithm to explore this design space.
 
@@
 This will reduce development costs and improve the quality of the final system.
-Additionally this approach enables the ranking of design alternatives with respect to conflicting NFP and the possibility to reuse these alternatives in other projects or products by using model transformations.
-In the future, we plan to integrate our approach in an existing framework RAMSES\footnote{Refinement of AADL Models for the Synthesis of Embdded Systems.
-\url{http://penelope.enst.fr/aadl/wiki/Projects}} which apply selection of design alternatives.
-Also evaluate our approach in more details quantitatively (i.e.
-experimenting it on a an industrial case study).
+Additionally this approach enables the ranking of design alternatives with respect to conflicting NFP and the possibility to reuse these alternatives in other projects or products by reusing model transformations.
+
+In the future, we plan to integrate our approach in the framework RAMSES and evaluating our approach in more details quantitatively (i.e. experimenting it on a an industrial case study)\cite{greg}.
 
@@
 
+\bibitem{greg}
+G.~Loniewski, E.~Borde, D.~Blouin and E.Insfran {\'{}}, ``An Automated Approach for Architectural Model
+  Transformations,'' in \emph{Information Systems
+  Development, 22nd International Conference, {ISD} 2013,
+  Sevilla, Spain, September 2013. Proceedings}, 2013, pp. 295-306.
+  [Online]. Available: \url{http://infres.enst.fr/~borde/isd2013loniewski.pdf}
+
 \bibitem{Medvidovic}
@@
 E.~Zitzler and S.~Künzli, ``Indicator-based selection in multiobjective
-  search,'' in \emph{in Proc. 8th International Conference on Parallel Problem
-  Solving from Nature (PPSN VIII}.\hskip 1em plus 0.5em minus 0.4em\relax
+  search,'' in \emph{in Proc. 22nd International Conference on Information Systems
+  Development (ISD 2013}.\hskip 1em plus 0.5em minus 0.4em\relax
   Springer, 2004, pp. 832--842.
+
+\bibitem{Koziolek:2011:PAA:2000259.2000267}
+A.~Koziolek, H.~Koziolek, and R.~Reussner, ``Peropteryx: Automated application
+  of tactics in multi-objective software architecture optimization,'' in
+  \emph{Proceedings of the Joint ACM SIGSOFT Conference -- QoSA and ACM SIGSOFT
+  Symposium -- ISARCS on Quality of Software Architectures -- QoSA and
+  Architecting Critical Systems -- ISARCS}, ser. QoSA-ISARCS '11.\hskip 1em
+  plus 0.5em minus 0.4em\relax New York, NY, USA: ACM, 2011, pp. 33--42.
+  [Online]. Available: \url{http://doi.acm.org/10.1145/2000259.2000267}
 

### 2014-10-29 SysCon_article/article_syscon.tex
paper modification of the section model transformation languages

@@
 \subsection{Model transformations languages}
-In general, model transformations are grouped into two main categories of model transformation languages : (i) rule-based transformation languages, or (ii)
-imperative transformation languages.
-We used in our work the first category of languages since it express model transformation logics in a way that is easy to interpret and \textbf{adapt} in other methods (in this paper MOEA).
-To be continued by giving more explanations about rule-based transformations languages
+In major cases, model transformations are grouped into two main categories of model transformation languages : (i) rule-based transformation languages, or (ii) imperative transformation languages\cite{Gorp06integratinga}.
 
-%Examples of rule-based transformation languages ATL (for Atlas Transformation Language) and QVT-R (for ).
+The first category express model transformation logics in a way that is easy to interpret and \textbf{adapt}.
+It permit to modify the pattern matching part of a transformation rule $TR$ which is sufficient to modify the set of elements this rule applies to.
+In contrary, the adaptation of imperative transformation languages are more difficult and requires a deep understanding of the control flow graph that leads to the execution of one or another transformation.
 
-%such as ATL and QVT-R, are of great interest in our context since they express model transformation logics in a way that is easy to interpret and adapt.
-Indeed, modifying the pattern matching part of a transformation rule is sufficient to modify the set of elements this rule applies to.
-In addition, superimposition helps to combine different sets of rules [15].
-Contrasting with rule-based formalisms, the adaptation of imperative transformation languages requires a deep understanding of the control flow graph that leads to the execution of one or another transformation.
-Model transformations we deal with in this paper are endogenous (AADL[13] to AADL model transformations) in order to refine or improve the architecture of an embedded system while representing the result of this refinement in an analyzable model (using AADL as an output language).
+We used in our work the first category of languages since it more easy to adapt in other methods (in this paper MOEA).
+Where model transformations are endogenous : the source and target models are the same.
+In our work we use a AADL to AADL model transformations in order to refine or improve the architecture of an embedded system while representing the result of this refinement in an analyzable model.
+More specific, we use the rule-based transformation language ATL (for Atlas Transformation Language).
+
+A rule-based transformation $T$ is generally composed of a set of transformation rules $(TR_{j}, j \in {1,2,..,n})$.
+Each transformation rule $TR_{j}$ is defined by a pair $<E_{j},R_{j}>$, where $E_{j}$ is the scope of the transformation rule $TR_{j}$ : the set of elements from the input model the transformation rule $TR_{j}$ can be applied to.
+And $R_{j}$ is the set of rules or actions which $TR_{j}$ executes when it is applied to an element of $E_{j}$ (i.e.
+creation of elements in the target model).
 
@@
 The architecture alternatives are formalized in a way that allow their reuse in different projects or products.
-To do so, we use model transformations methods.
+To do so, we use model transformations mechanisms.
 An issue in using such methods is their complexity : how to identify which elements of the input architecture model transformation alternatives can be applied.
-To ease the development and maintenance of such model transformations, we propose to use a rule-based transformation language and composition mechanisms.
-These languages define rules which define the mapping from source elements (elements of the software architecture) to target element (architecture alternative).
+To ease the development and maintenance of such model transformations, we propose to use a rule-based transformation languages and composition mechanisms.
 
-In our approach we call these rules TRA (Transformation Rules Alternatives).
+In our approach we have several Transformation Rules Alternatives (TRA).
 They represent the genomes to optimize in our multi-objective problem.
@@
 Each $TRA_{i}$ is, in turn, encoded as a pair $TRA_{i} = <Elements_{i},Rule_{i}>$ where $Elements_{i} (i ={1,2,...,n})$ is a list of elements from the input model, and $Rule_{i} (i ={1,2,...,n})$ is a transformation rule which can be applied to $Elements_{i}$.
+
+%These languages define rules which define the mapping from source elements (elements of the software architecture) to target element (architecture alternative).
 
@@
 
+\subsection{model transformations techniques}
+Recently, several works
+
+\subsection{multi-objective metaheuristic optimization}
 Aleti et al.\cite{Gr5069138} have developed the ArchOpteryx framework.
@@
 
+\bibitem{Gorp06integratinga}
+P.~V. Gorp, O.~Muliawan, D.~Janssens, P.~V. Gorp, O.~Muliawan, and D.~Janssens,
+  ``Integrating a declarative with an imperative model transformation
+  language,'' 2006.
+
 \bibitem{Johnsen1753}

### 2014-10-29 SysCon_article/article_syscon.tex
modification of the section related work

@@
 
-%modeling solution for their application, platform, and mapping between application and platform, in an integrated and simultaneous way and at a very early design stage, before system synthesis and code generation have been performed.
-
-%multi-objective optimization evolutionary algorithms which is known to be an important tool for design decision making support.
-
-%The design of safety-critical systems becomes one of the most interesting challenges in modern systems engineering.
-It requires system architects to address a large number of non-functional properties related to performance, reliability, availability and temporal performance.
-Moreover, these non-functional properties often conflict with each other, for instance, improving system performance often needs more powerful hardware components, which increases the production cost and power consumption in the meantime.
-
-%and model transformation strategies to identify a sufficient set of design alternatives.
-This approach will reduce development costs and improve the quality of the final system, because an automated and systematic search will identify more and better design alternatives.
-
-%In this paper, we propose an approach which can analyse a given system architecture, propose design alternatives to it by using model transformations, and do architecture optimization by using some evolutionary algorithms to improve its non-functional properties in an automatic way.
 \end{abstract}
-
-%This paper proposes to use multi-objective optimization evolutionary algorithms and model transformation strategies to identify a sufficient set of design alternatives.
-This approach will reduce development costs and improve the quality of the final system, because an automated and systematic search will identify more and better design alternatives.
-
-% no keywords
 
@@
 Section~\ref{Related} presents the related work.
-%The remainder of this paper is organized as follows.
-Section~\ref{Problem} is dedicated to the problem statement.
-Section~\ref{Approach} gives an overview  of our approach.
-While Section~\ref{Adapting} details our approach.
-Section~\ref{Related} presents the related work.
-Finally, conclusions and perspectives are given in Section~\ref{Conclu}.
 
@@
 To formalize these design patterns in a way that allow their reuse in different projects or products we implement them as model transformations.
-
-%These design patterns are implemented as model transformations. It  which allows us to applied them to various sets of NFP
-
-%improving a set NFP, and solving the conflict between these NFP.
-Model transformations are usually defined to be generic such as design patterns which allows us to applied them to various sets of NFP.
-
-%A set of model transformations that implement refinements or improvements of the source model, each of them focusing on increasing the satisfaction of a given goal (reducing power consumption, increasing availability, etc.).
-These model transformations can be seen as design patterns, each of them implementing a well-known solution to a given quality objective.
-
-%A possible solution to this issue is to formalize design alternatives so they can be reusable in different products or projects (i.e.
-by using model transformation techniques).
-After the formalization step, explore the design space to identify the set of optimal model transformation alternatives : solutions that fulfils most NFP.
 
@@
 \subsection{System architecture modelisation}
-%For software architecture modeling step, as a natural extension of previous work RAMSES and  we choose to use AADL (Architecture Analysis & Design Language) as the underlying architecture description language.
-
 Since our application domain is embedded systems, we have chosen AADL (Architecture Analysis \& Design Language) as the underlying architecture description language.
@@
 
-%These languages define rules which define the mapping from source elements (elements of the software architecture) to target element (architecture alternative).
-
 \begin{figure}[!t]
@@
 The more fit genomes are stochastically selected from the current population, and each genome is modified (recombined and possibly randomly mutated) to form a new generation.
-
-%\subsection{Adapting NSGA-II To explore the design space}
-%The second step of our approach consists in (i) the exploration of the design space (composed of the set of genomes described above); and (ii) selection of the optimal genomes.
-This step is realised by adapting the concepts of the NSGA-II algorithm to our design problem.
-To do so, we use the same algorithm as described previously.
-Except that each genome is represented by a set of TRA.
 
@@
 
-%In the genetic algorithm used in the evolutionary design system above the genotypes consist of 1's and 0's, applying the mutation operator to a genotype of this kind switches a randomly selected 1 to a 0 or vice versa.
-%Indicating the core in the tile TRA as cs and ct as the core with which cs communicates most frequently, cs is remapped on a tile adjacent to Ts so as to reduce the distance between cs and ct .
-thus obtaining the mutated chromosome C0.
-
 \begin{figure}[!t]
@@
 
-%\subsection{\textbf{Use case}}
-%Figure~\ref{nsgaDesign} gives an overview of the application of
-
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=3.49in]{nsgaDesign.pdf}
-%\caption{Overview of the adaptation of NSGA-II}
-%\label{nsgaDesign}
-%\end{figure}
-
 \section{Related Work}
@@
 \subsection{model transformations techniques}
-Recently, several works
+Recently, some works have focused on the definition of model transformation alternatives.
+The first works introduced the superimposition mechanism\cite{Navarro:2011:UMT:2041790.2041840} to implement transformations alternatives.
+Another work\cite{Kavimandan:2011:MQS:2000259.2000264} proposed to implement transformations alternatives by using rule-based transformation languages.
+These works has been continued in\cite{Drago:2011} in order to deal with architecture quality problems.
+
+Our contribution is based on this work since it enable the factorization and composition of model transformations.
+However, this approach doesn't propose any algorithm to select the non-dominated (or pareto) model transformations alternatives which fulfil at best a set of competing non-functional properties.
 
@@
 Aleti et al.\cite{Gr5069138} have developed the ArchOpteryx framework.
-ArchOpteryx assists the system architects during the design to create architectures that meet non-functional properties by using multi-objective optimization strategies.
-Unlike this method, design alternatives are implemented as model transformations driven by NFP.
-Using model transformations help the design architects to (i) automating the system production; (ii) reusing architecture alternatives in other projects (or products) and (iii) solving the competition issue between NFP.
+ArchOpteryx assists the system architects during the design phase to create architectures that meet non-functional properties by using multi-objective optimization strategies.
+
+Koziolek et al.\cite{Koziolek:2011:PAA:2000259.2000267} also developed their own framework Peropteryx for improvement of system architecture models using a metaheuristic search guided by architectural tactics.
+
+Unlike these two frameworks, in our approach design alternatives are implemented as model transformations driven by NFP.
+The use of model transformations help the design architects to (i) automating the system production; (ii) reusing architecture alternatives in other projects (or products) and (iii) solving the competition issue between NFP.
+
 Compared to DesignBots\cite{Diaz-Pace:2007:UPT:1784860.1784865}, in our method model transformations are not decomposed into subplans, each transformation is performed atomically.
-
-Koziolek et al.\cite{Koziolek:2011:PAA:2000259.2000267} have developed the Peropteryx framework for improvement of system architecture models using a metaheuristic search guided by architectural tactics.
 
@@
 In the future, we plan to integrate our approach in the framework RAMSES and evaluating our approach in more details quantitatively (i.e. experimenting it on a an industrial case study)\cite{greg}.
-
-%Older works and experiments have shown that evolutionary algorithms and multiobjective optimization strategies can be used to identify Pareto-optimal or near Pareto-optimal architecture designs, which can be used as an input for architecture trade-off analysis techniques.
-
-%The main benefit of this approach is the ability to handle the large search spaces of quality optimization problems and to automate the identification of good architecture design alternatives.
-This will reduce development costs and improve the quality of the final system.
-Addition- ally this approach enables the ranking of design decisions (architectural refactorings) with respect to conflicting quality requirements.
 
@@
 
+\bibitem{Drago:2011}
+M.~Drago, C.~Ghezzi, and R.~Mirandola, ``Towards quality driven exploration of
+  model transformation spaces,'' in \emph{Model Driven Engineering Languages
+  and Systems}, ser. Lecture Notes in Computer Science, J.~Whittle, T.~Clark,
+  and T.~Kühne, Eds., vol. 6981.\hskip 1em plus 0.5em minus 0.4em\relax
+  Springer Berlin Heidelberg, 2011, pp. 2--16. [Online]. Available:
+  \url{http://dx.doi.org/10.1007/978-3-642-24485-8_2}
+
 \bibitem{Gorp06integratinga}
@@
   language,'' 2006.
+
+\bibitem{greg}
+G.~Loniewski, E.~Borde, D.~Blouin and E.Insfran {\'{}}, ``An Automated Approach for Architectural Model
+  Transformations,'' in \emph{Information Systems
+  Development, 22nd International Conference, {ISD} 2013,
+  Sevilla, Spain, September 2013. Proceedings}, 2013, pp. 295-306.
+  [Online]. Available: \url{http://infres.enst.fr/~borde/isd2013loniewski.pdf}
 
@@
 
+\bibitem{Kavimandan:2011:MQS:2000259.2000264}
+A.~Kavimandan, A.~Gokhale, G.~Karsai, and J.~Gray, ``Managing the quality of
+  software product line architectures through reusable model transformations,''
+  in \emph{Proceedings of the Joint ACM SIGSOFT Conference -- QoSA and ACM
+  SIGSOFT Symposium -- ISARCS on Quality of Software Architectures -- QoSA and
+  Architecting Critical Systems -- ISARCS}, ser. QoSA-ISARCS '11.\hskip 1em
+  plus 0.5em minus 0.4em\relax New York, NY, USA: ACM, 2011, pp. 13--22.
+  [Online]. Available: \url{http://doi.acm.org/10.1145/2000259.2000264}
+
 \bibitem{Kleppe2003}
@@
 
-\bibitem{greg}
-G.~Loniewski, E.~Borde, D.~Blouin and E.Insfran {\'{}}, ``An Automated Approach for Architectural Model
-  Transformations,'' in \emph{Information Systems
-  Development, 22nd International Conference, {ISD} 2013,
-  Sevilla, Spain, September 2013. Proceedings}, 2013, pp. 295-306.
-  [Online]. Available: \url{http://infres.enst.fr/~borde/isd2013loniewski.pdf}
+\bibitem{Koziolek:2011:PAA:2000259.2000267}
+A.~Koziolek, H.~Koziolek, and R.~Reussner, ``Peropteryx: Automated application
+  of tactics in multi-objective software architecture optimization,'' in
+  \emph{Proceedings of the Joint ACM SIGSOFT Conference -- QoSA and ACM SIGSOFT
+  Symposium -- ISARCS on Quality of Software Architectures -- QoSA and
+  Architecting Critical Systems -- ISARCS}, ser. QoSA-ISARCS '11.\hskip 1em
+  plus 0.5em minus 0.4em\relax New York, NY, USA: ACM, 2011, pp. 33--42.
+  [Online]. Available: \url{http://doi.acm.org/10.1145/2000259.2000267}
 
@@
   \url{http://dx.doi.org/10.1109/32.825767}
+
+\bibitem{Navarro:2011:UMT:2041790.2041840}
+E.~Navarro, C.~E. Cuesta, D.~E. Perry, and C.~Roda, ``Using model
+  transformation techniques for the superimposition of architectural styles,''
+  in \emph{Proceedings of the 5th European Conference on Software
+  Architecture}, ser. ECSA'11.\hskip 1em plus 0.5em minus 0.4em\relax Berlin,
+  Heidelberg: Springer-Verlag, 2011, pp. 379--387. [Online]. Available:
+  \url{http://dl.acm.org/citation.cfm?id=2041790.2041840}
 
@@
 
-\bibitem{Koziolek:2011:PAA:2000259.2000267}
-A.~Koziolek, H.~Koziolek, and R.~Reussner, ``Peropteryx: Automated application
-  of tactics in multi-objective software architecture optimization,'' in
-  \emph{Proceedings of the Joint ACM SIGSOFT Conference -- QoSA and ACM SIGSOFT
-  Symposium -- ISARCS on Quality of Software Architectures -- QoSA and
-  Architecting Critical Systems -- ISARCS}, ser. QoSA-ISARCS '11.\hskip 1em
-  plus 0.5em minus 0.4em\relax New York, NY, USA: ACM, 2011, pp. 33--42.
-  [Online]. Available: \url{http://doi.acm.org/10.1145/2000259.2000267}
-
 \end{thebibliography}

### 2014-10-29 SysCon_article/article_syscon.tex
replacement of all the figures

@@
 
-\begin{figure}[!t]
+\begin{figure}[!ht]
 \centering
@@
 \subsection{Genome representation}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=3.49in]{genome.pdf}
+\caption{Genome overview}
+\label{genome}
+\end{figure}
+
 The first step of our work consists in applying the definition of the multi-objective optimization problem on our architecture design problem.
@@
 Each $TRA_{i}$ is, in turn, encoded as a pair $TRA_{i} = <Elements_{i},Rule_{i}>$ where $Elements_{i} (i ={1,2,...,n})$ is a list of elements from the input model, and $Rule_{i} (i ={1,2,...,n})$ is a transformation rule which can be applied to $Elements_{i}$.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.49in]{genome.pdf}
-\caption{Genome overview}
-\label{genome}
-\end{figure}
 
@@
 
-Figure~\ref{binary} illustrates this operation.
-On this figure, we suppose we have four genomes (G1,G2,G3,G4) and we apply two tournaments to produce the needed genomes.
-The final genomes of the competition will always be the fittest genomes in the population.
-The more successful the genome is in competition, the more often that genome is expected to appear in the mating pool (In Figure~\ref{binary} the fittest genome is G4).
-
-\begin{figure}[!t]
+\begin{figure}[!ht]
 \centering
@@
 
+Figure~\ref{binary} illustrates this operation.
+On this figure, we suppose we have four genomes (G1,G2,G3,G4) and we apply two tournaments to produce the needed genomes.
+The final genomes of the competition will always be the fittest genomes in the population.
+The more successful the genome is in competition, the more often that genome is expected to appear in the mating pool (In Figure~\ref{binary} the fittest genome is G4).
+
 \subsubsection{\textbf{Crossover}}
@@
 
-Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes G1 and G2 respectively composed of \{TRA11,TRA12,TRA13\} and \{TRA21,TRA22,TRA23\} to produce a new genome G3.
-As can be seen in Figure~\ref{crossover}, this operator combines G1 and G2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.
-
-\begin{figure}[!t]
+\begin{figure}[!ht]
 \centering
@@
 
+Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes G1 and G2 respectively composed of \{TRA11,TRA12,TRA13\} and \{TRA21,TRA22,TRA23\} to produce a new genome G3.
+As can be seen in Figure~\ref{crossover}, this operator combines G1 and G2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.
+
 \subsubsection{\textbf{Mutation}}
 After performing the crossover, the obtained solutions could be mutated with a given mutation probability.
-The mutation operator act on a single genome G1 to obtained a muted genome G11 acts as follows.
-The mutation operator selects a gene at random in the genome and changes its value.
-In Figure~\ref{mutation}, the third tile TRA13 is selected to mutate into TRA14 : we apply a different rule (i.e.
-rule4) to the set of selected elements.
 
-\begin{figure}[!t]
+\begin{figure}[!ht]
 \centering
@@
 \end{figure}
+
+The mutation operator act on a single genome G1 to obtained a muted genome G11 acts as follows.
+The mutation operator selects a gene at random in the genome and changes its value.
+In Figure~\ref{mutation}, the third tile TRA13 is selected to mutate into TRA14 : we apply a different rule (i.e.
+rule4) to the set of selected elements.
 

### 2014-10-30 SysCon_article/article_syscon.tex
adding a new section for EMOA definitions and applying some modification on the paper

@@
 
-\author{\IEEEauthorblockN{Smail Rahmoun}
-\IEEEauthorblockA{Institute for Technological Research\\SystemX\\
-Palaiseau France\\
-Email: smail.rahmoun@irt-systemx.fr}
-\and
-\IEEEauthorblockN{Etienne Borde\\ and Laurent Pautet}
-\IEEEauthorblockA{TELECOM Paristech Institut\\
-LTCI-UMR 5141\\
-Paris, France\\
-Email: firstname.name@telecom-paristech.fr}}
+%\author{\IEEEauthorblockN{Smail Rahmoun}
+%\IEEEauthorblockA{Institute for Technological Research\\SystemX\\
+%Palaiseau France\\
+%Email: smail.rahmoun@irt-systemx.fr}
+%\and
+%\IEEEauthorblockN{Etienne Borde\\ and Laurent Pautet}
+%\IEEEauthorblockA{TELECOM Paristech Institut\\
+%LTCI-UMR 5141\\
+%Paris, France\\
+%Email: firstname.name@telecom-paristech.fr}}
+ \author{\IEEEauthorblockN{
+  Smail Rahmoun\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
+  Etienne Borde\IEEEauthorrefmark{2},
+  Laurent Pautet\IEEEauthorrefmark{2},
+}
+
+\IEEEauthorblockA{\IEEEauthorrefmark{1}Institute for Technological Research SystemX
+                - 8, Avenue de la Vauve 91120 PALAISEAU\\
+                % Palaiseau France\\
+                smail.rahmoun@irt-systemx.fr}
+
+\IEEEauthorblockA{\IEEEauthorrefmark{2}Institut Telecom;TELECOM ParisTech; LTCI - UMR 5141
+                - 46 rue Barrault, 75013 Paris, France\\
+                firstname.lastname@telecom-paristech.fr}
+
+}
 
@@
 
-\subsection{Multi-Objective Genetic Algorithm}
+\subsection{Multi-Objective Evolutionary Algorithm}
 In order to deal with the multi-objective nature of our problem (which model transformation achieve the best possible trade-off among NFP) we use MOEA. 
@@
 It was proposed in the early 90's and still considered today as one of the state-of-the-art MOEA for its robustness across a variety of application domain.
+
+\subsubsection{\textbf{Definitions}}
+An evolutionary algorithm (EA) is characterized by three features :
+\begin{itemize}
+\item a set of solution candidates is maintained,
+\item a mating selection process is performed on this set, and
+\item several solutions may be combined in terms of recombination to generate new solutions.
+\end{itemize}
+
+The solution candidates are called \textbf{genomes} (or individuals) and the set of solution candidates is called the \textbf{population}.
+Each genome represents a possible solution, i.e., a decision vector, to the problem at hand; however, a genome is not a decision vector but rather encodes it based on an appropriate representation.
+
+The mating selection process usually consists of two steps: \textbf{fitness evaluation} and \textbf{mating pool}.
+In the first step, the genomes are evaluated in the objective space and then assigned a scalar value called \textbf{fitness}, reflecting their quality.
+Afterwards, a mating pool is created by random sampling from the population according to the fitness values.
+For example using a binary tournament selection.
+Where two genomes are randomly chosen from the population, and the one with the better fitness value is copied to the mating pool.
+This procedure is repeated until the mating pool is filled.
+
+Then, the variation operators are applied to the mating pool.
+Usually these operators are called \textbf{genetic operators}.
+With EAs, there are two operators namely the crossover (or recombination) and the mutation.
+
+%here badness
+Based on the above concepts, EAs are simulated by an iterative computation process.
+First, an initial population is created at random, which is the starting point of the evolution process.
+Then a loop consisting of the fitness evaluation, selection, genetic operators is executed a certain number of times.
+Each loop iteration is called a generation, and often a predefined maximum number of generations serves as the termination criterion of the loop.
 
@@
 
-\subsection{Genome evaluation}
+\subsection{Fitness evaluation of each genome}
 In each generation, the fitness of every genome in the population is evaluated.
@@
 Figure~\ref{binary} illustrates this operation.
-On this figure, we suppose we have four genomes (G1,G2,G3,G4) and we apply two tournaments to produce the needed genomes.
+On this figure, we suppose we have four genomes G1,G2,G3 and G4 respectively composed of TRA11,TRA21,TRA31 and TRA41.
+We apply two tournaments between paired genomes to produce the needed genomes.
+In the first round we have two tournaments between two different pairs of genomes (G1 with G2 and G3 with G4).
+In the second round we apply another tournament on the victorious genomes in the previous round (G2 and G4) .
+
 The final genomes of the competition will always be the fittest genomes in the population.
@@
 Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes G1 and G2 respectively composed of \{TRA11,TRA12,TRA13\} and \{TRA21,TRA22,TRA23\} to produce a new genome G3.
-As can be seen in Figure~\ref{crossover}, this operator combines G1 and G2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.
+As can be seen in Figure~\ref{crossover}, this operator combines TRA11 from G1 and {TRA22,TRA23} from G2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.
 

### 2014-10-30 SysCon_article/article_syscon.tex
modification of all the paper

@@
                 % Palaiseau France\\
-                smail.rahmoun@irt-systemx.fr}
+                firstname.lastname@irt-systemx.fr}
 
@@
 The size and complexity of modern systems is rapidly increasing. Meanwhile, the ability to understand and maintain such systems is decreasing almost as fast.
-Model Driven Engineering (MDE) promotes the automation of design activities by means of model transformations, enabling to cope with systems complexity.
+Model Driven Engineering promotes the automation of design activities by means of model transformations, enabling to cope with systems complexity.
 However, the design space produced by the composition of these model transformations is difficult to explore automatically.
@@
 This paper presents a MDA approach for design space exploration to deal with the ever-growing challenge of designing complex embedded systems.
-This approach allows the system architects to automatically select the most adequate model transformations compositions by using multi-objectives optimization evolutionary algorithms (MOEA) mechanisms.
+This approach allows the system architects to automatically select the most adequate model transformations compositions by using multi-objectives optimization evolutionary algorithms.
 
@@
 Nowadays, modern systems become more and more large and complex and therefore more difficult to develop and maintain.
-For example, embedded critical systems which are often built to accomplish specific functionalities, can integrate thousands of buses, software and hardware components.
-To guarantee properties such as safety, availability and robustness makes the design of these systems very challenging and complicated.
+For example, embedded critical systems which are often built to accomplish specific functionalities, can integrate several buses, software and hardware components.
+To guarantee properties such as safety, availability and robustness makes the design of these systems very challenging.
 
-Model Driven Engineering (MDE) proposes the use of models as the key assets in the development of such systems, and hence all sorts of model modifications are needed.
-In this way, model transformations become one of the basic building blocks of MDE.
+Model Driven Engineering (MDE) proposes the use of models as the key assets in the development of such systems.
+Model transformations approach become one of the basic building blocks of MDE.
 Even though MDE is being successfully applied in many scenarios, it still needs appropriate mechanisms to handle the development of complex, large-scale systems.
@@
 In this work, we use generic model transformation to model design alternatives of the system.
-This process will help us to predict NFP of a system before it development\cite{1291833}.
+This process will help us to predict non-functional properties (NFP) of a system before its development\cite{1291833}.
 This prediction can be exploited to drive decisions about which components should be used and how they should be connected so as to meet the NFP imposed on the design.
 
-Moreover, an issue in modeling the NFP of a system is that, the NFP could conflict\footnote{improving one property can have a negative impact on other properties} with each other.
+Moreover, an issue in modeling a system is that, the NFP could conflict\footnote{improving one property can have a negative impact on other properties} with each other.
 For example, improving the availability of a service is often done by replication of the service, which causes the increasing of the response time of these services\cite{Yu:2001:CLA:502059.502038}.
 Developing a system that satisfies at best all its NFP simultaneously is often not possible : improving a NFP of a system can deteriorate another NFP.
-As a consequence, system architects have to come up with several design alternatives and select the optimal solution (Pareto optimal solutions) from all feasible alternatives through the trade-off analysis regarding all NFP\cite{Coello98acomprehensive}.
+As a consequence, system architects have to come up with several design alternatives and select the solutions which fulfils at best all NFP\cite{Coello98acomprehensive} simultaneously from all feasible alternatives.
+The selected solutions are called non-dominated solutions or Pareto optimal solutions : a solution x2 is non-dominated by another solution x1, if x2 matches or exceeds x1 in all objectives (NFP).
 
 In order to obtain the set of Pareto optimal alternatives, some advanced multi-objective optimization evolutionary algorithms (MOEA) have been proposed.
-These algorithm apply some fitness evaluations and generic operators of variation.
+These algorithms apply some fitness evaluations and generic operators of variation.
 Thus, they are applicable to search spaces (e.g.
@@
 prediction of NFP).
-MOEA also provides selection operators which guide the search towards interesting regions of the search space by (i) favorizing non-dominated solutions : where a solution x1 is dominated by another solution x2 , if x2 matches or exceeds x1 in all objectives; (ii) finding a diverse set of solutions on the Pareto front.
+MOEA also provides selection operators which guide the search towards interesting regions of the search space by (i) favorizing non-dominated solutions; and (ii) finding a diverse set of solutions on the Pareto front..
 
-Our approach, consists in improving the NFP of an architecture design through a generic method using model transformations compositions and advanced MOEA.
+In this paper, we introduce an approach, tailored for embedded system architecture design, where architecture alternatives are implemented as model transformations driven by NFPs.
+And to find good transformations alternatives that help system architects perform trade-off analysis, we use some advanced MOEA.
+More specific, we adapt (or map) model transformations mechanisms into a multiple-objective optimization problem.
+
+%Our approach, consists in improving the NFP of an architecture design through a generic method using model transformations compositions and advanced MOEA.
 This method will automate the search for optimal compositions from all feasible alternatives.
@@
 To construct a system that fulfils all its NFP simultaneously is often not possible.
-As a consequence, system architects have to consider several design alternatives, and identify a solution that fulfils most NFP (an optimal solution) from all feasible alternatives.
+As a consequence, system architects have to consider several design alternatives, and identify a solution that fulfils most NFP from all feasible alternatives.
 
 A possible solution to this issue is to implement these design alternatives in a way that they can be seen as design patterns.
-Where each pattern implement a well-known architectural solution which fulfils a set of NFP.
-To formalize these design patterns in a way that allow their reuse in different projects or products we implement them as model transformations.
+Each pattern implements a well-known architectural solution which fulfils a set of NFP.
+To formalize these design patterns in a way that allows their reuse in different projects or products we implement them as model transformations.
 
@@
 The exploration of such design space can be very difficult to do manually and error-prone.
-To overcome this issue, we propose an approach to assist architects throughout the modeling phase and automate the design space exploration by using existing multiple objective evolutionary algorithms (MOEA).
+To overcome this issue, we propose an approach to assist architects throughout the modeling phase and automate the design space exploration by using advanced MOEA.
 
 Moreover, using MOEA to deal with mode transformations alternatives can be challenging.
-We have (i) to generalize the architecture design problem as a multiple objective optimization problem; (ii) select the more suitable evolutionary algorithm to solve this optimization problem; and (iii) adapting the notions of model transformation compositions to this evolutionary algorithm.
+We have (i) to generalize the architecture design problem as a multiple objective optimization problem; (ii) select the more suitable evolutionary algorithm to solve this optimization problem; and (iii) adapt the notions of model transformation techniques to this evolutionary algorithm.
 
-\section{Using evolutionary algorithms for identifying good design alternatives}
-\label{Approach}
-Figure~\ref{IS} graphically illustrates the approach proposed in this paper by showing the process underlying it.
-As can be seen in Figure~\ref{IS}, the process starts with an initial input software architecture which could be designed by software architects by using some architecture design language\cite{Medvidovic}.
-After that, this architecture model is transformed into a set of alternative architecture models (more detailed models) which fulfils a set of competing NFP such as reliability, availability and response time.
-To solve the trade-off between NFP we expressed the architecture alternatives as design patterns implemented by means of model transformations and compositions techniques.
-The final step in Figure~\ref{IS} consists in exploring the design space composed of all model transformation compositions and select which transformation fulfil at best the NFP of the system.
-This step is done by using an advanced evolutionary algorithm.
+\section{Multi-Objective Evolutionary Algorithm}
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.49in]{IDMT.pdf}
-\caption{Overview of the identification step}
-\label{IS}
-\end{figure}
-
-\subsection{System architecture modelisation}
-Since our application domain is embedded systems, we have chosen AADL (Architecture Analysis \& Design Language) as the underlying architecture description language.
-AADL has been designed on the foundation of the architecture description language MetaH and its goals are (i) specification of quality analysis (e.g.
-safety); and (ii) design architectures for complex embedded systems.
-It offers a standardized semantics, mostly expressed using natural language and the components are composed hierarchically according to standardized composition rules.
-AADL also allows the designers to expand model by defining new property sets in their own specific way.
-The other reason of choosing AADL is to integrate our work in an existing framework RAMSES\footnote{Refinement of AADL Models for the Synthesis of Embdded Systems.
-\url{http://penelope.enst.fr/aadl/wiki/Projects}} which apply selection of design alternatives.
-
-\subsection{Multi-Objective Evolutionary Algorithm}
-In order to deal with the multi-objective nature of our problem (which model transformation achieve the best possible trade-off among NFP) we use MOEA. 
-Among the many MOEAs that have been proposed in the literature : NSGA-II\cite{Deb:2002:FEM:2221359.2221582}, SPEA2\cite{Zitzler01spea2:improving}, IBEA\cite{Zitzler04indicatorbasedselection}, only one have been considered in this work, namely NSGA-II (Non-dominated Sorting Genetic Algorithm).
-It was proposed in the early 90's and still considered today as one of the state-of-the-art MOEA for its robustness across a variety of application domain.
-
-\subsubsection{\textbf{Definitions}}
-An evolutionary algorithm (EA) is characterized by three features :
-\begin{itemize}
-\item a set of solution candidates is maintained,
-\item a mating selection process is performed on this set, and
-\item several solutions may be combined in terms of recombination to generate new solutions.
-\end{itemize}
+An evolutionary algorithm (EA) is characterized by three features : (i) a set of solution candidates is maintained; (ii) a mating selection process is performed on this set, and (iii) several solutions may be combined in terms of recombination to generate new solutions.
 
 The solution candidates are called \textbf{genomes} (or individuals) and the set of solution candidates is called the \textbf{population}.
-Each genome represents a possible solution, i.e., a decision vector, to the problem at hand; however, a genome is not a decision vector but rather encodes it based on an appropriate representation.
+Each genome is composed of a sequence of genes and represents a possible solution to the problem at hand.
 
@@
 
-Then, the variation operators are applied to the mating pool.
+Then, the variation operators are applied to the mating pool to obtain better solutions.
 Usually these operators are called \textbf{genetic operators}.
@@
 
-%here badness
 Based on the above concepts, EAs are simulated by an iterative computation process.
@@
 Each loop iteration is called a generation, and often a predefined maximum number of generations serves as the termination criterion of the loop.
+
+In order to deal with the multi-objectives nature of our problem (which model transformations achieve the best possible trade-off among NFP) we use MOEA. 
+Among the many MOEAs that have been proposed in the literature : NSGA-II\cite{Deb:2002:FEM:2221359.2221582}, SPEA2\cite{Zitzler01spea2:improving}, IBEA\cite{Zitzler04indicatorbasedselection}, only one has been considered in this work, namely NSGA-II (Non-dominated Sorting Genetic Algorithm).
+It was proposed in the early 90's and still considered today as one of the state-of-the-art MOEA for its robustness across a variety of application domain.
 
@@
 \begin{enumerate}
-\item Initially, Create a random parent population $P_{0}$ composed of N genomes (N = 3 in Figure~\ref{nsgaii}).
+\item Initially, Create a random parent population $P_{0}$ composed of N genomes (N = 3 in Figure~\ref{nsgaii}). N represent the size of the population.
 \item Sort the current population based on a non domination criterion (e.g. reliability, availability and response time).
@@
 \item From the first generation onwards, creation of each new generation constitutes the following steps :
-	\begin{enumerate}	
-	\item Create the mating pool $R_{t}$ of size 2N by combining the parent population $P_{t}$ and the child population $Q_{t}$.
-	\item Sort the combined population $R_{t}$ according to the fast non-dominated sorting procedure to identify all non-dominated fronts $(F_{1} ,F_{2},...,F_{k})$.
-	\item Generate the new parent population $P_{t}+1$ of size N by adding non-dominated solutions starting from the first ranked non-dominated front $F1$ and proceeding with the subsequently ranked non-dominated fronts $F_{1} ,F_{2}, .
+\item[5.a)] Create the mating pool $R_{t}$ of size 2N by combining the parent population $P_{t}$ and the child population $Q_{t}$.
+\item[5.b)] Sort the combined population $R_{t}$ according to the fast non-dominated sorting procedure to identify all non-dominated fronts $(F_{1} ,F_{2},...,F_{k})$.
+\item[5.c)] Generate the new parent population $P_{t}+1$ of size N by adding non-dominated solutions starting from the first ranked non-dominated front $F1$ and proceeding with the subsequently ranked non-dominated fronts $F_{1} ,F_{2}, .
 .
@@
 \item Perform the selection, crossover and mutation operations on the newly generated parent population $(P_{t}+1)$ to create the new child population $(Q_{t}+1)$) of size N (Figure~\ref{nsgaii}).
-	\end{enumerate}
 \item Repeat Step 5 until a stopping criterion is met (e.g. maximum number of generations is reached).
@@
 
-\section{Compose model transformation alternatives by using NSGA-II}
-\label{Adapting}
+\section{Using evolutionary algorithms for identifying best design alternatives}
+\label{Approach}
+Figure~\ref{IS} graphically illustrates the approach proposed in this paper by showing the process underlying it.
+As can be seen in Figure~\ref{IS}, the process starts with an initial input software architecture which could be designed by software architects by using architecture design languages\cite{Medvidovic}.
+After that, the input model is transformed into a set of alternative architecture models (more detailed models) driven by a set of competing NFP.
+To solve the trade-off between NFP we expressed the architecture alternatives as design patterns implemented by means of model transformations and compositions techniques.
+The next step consists at finding the best model transformations alternatives.
+To do so we (i) map these model transformations alternatives as a multiple-objectives optimization problem and (ii) use NSGA-II to find the non-dominated solutions.
 
-In this paper we propose a generic method to automate the search of optimal architectures (which fulfil at best the NFP of the system) from the design space.
-To represent the design space (set of architecture alternatives) we use model transformations compositions.
-The exploration step is done by using the NSGA-II algorithm.
+%The final step in Figure~\ref{IS} consists in exploring the design space composed of all model transformation compositions and select which transformation fulfil at best the NFP of the system.
+This step is done by using an advanced evolutionary algorithm.
 
-\subsection{Model transformations languages}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=3.49in]{IDMT.pdf}
+\caption{Approach overview}
+\label{IS}
+\end{figure}
+
+\subsection{System architecture modelisation}
+Since our application domain is embedded systems, we have chosen AADL (Architecture Analysis \& Design Language) as the underlying architecture description language.
+AADL has been designed on the foundation of the architecture description language MetaH and its goals are (i) specification of quality analysis (e.g.
+safety); and (ii) design architectures for complex embedded systems.
+It offers a standardized semantics, mostly expressed using natural language and the components are composed hierarchically according to standardized composition rules.
+AADL also allows the designers to expand model by defining new property sets in their own specific way.
+The other reason of choosing AADL is to integrate our work in an existing framework RAMSES\footnote{Refinement of AADL Models for the Synthesis of Embdded Systems.
+\url{http://penelope.enst.fr/aadl/wiki/Projects}} which apply selection of design alternatives.
+
+\subsection{Model transformations composition}
+\label{transfos}
 In major cases, model transformations are grouped into two main categories of model transformation languages : (i) rule-based transformation languages, or (ii) imperative transformation languages\cite{Gorp06integratinga}.
@@
 
-We used in our work the first category of languages since it more easy to adapt in other methods (in this paper MOEA).
+We used in our work the first category of languages since it more easy to adapt into other methods (in this paper MOEA).
 Where model transformations are endogenous : the source and target models are the same.
-In our work we use a AADL to AADL model transformations in order to refine or improve the architecture of an embedded system while representing the result of this refinement in an analyzable model.
+In our work we use a AADL to AADL model transformations in order to improve (or refine) the architecture of an embedded system while representing the result of this refinement in an analysable model.
 More specific, we use the rule-based transformation language ATL (for Atlas Transformation Language).
 
-A rule-based transformation $T$ is generally composed of a set of transformation rules $(TR_{j}, j \in {1,2,..,n})$.
-Each transformation rule $TR_{j}$ is defined by a pair $<E_{j},R_{j}>$, where $E_{j}$ is the scope of the transformation rule $TR_{j}$ : the set of elements from the input model the transformation rule $TR_{j}$ can be applied to.
-And $R_{j}$ is the set of rules or actions which $TR_{j}$ executes when it is applied to an element of $E_{j}$ (i.e.
+A model transformation $MT$ is generally composed of a set of transformation rules $(TR_{i})$.
+Each transformation rule $TR_{i}$ is defined by a pair $<E_{j},R_{j}>$, where $E_{j}$ is the scope of the transformation rule $TR_{i}$ : the set of elements from the input model the transformation rule $TR_{i}$ can be applied to.
+And $R_{j}$ is the set of rules or actions which $TR_{i}$ executes when it is applied to an element of $E_{j}$ (i.e.
 creation of elements in the target model).
 
-\subsection{Genome representation}
+%In the second step of this approach, we use the rule-based transformation language ATL (for Atlas Transformation Language), where architecture alternatives are implemented as model transformations driven by NFPs.
+
+\subsection{Mapping model transformation alternatives into a multiple-objectives optimization problem}
+\label{Adapting}
+
+The next step of our approach consist in using model transformations definitions described in Section~\ref{transfos} and integrate them into a multiple-objectives optimization problem.
+Where the population to optimize or the design space represent a set of model transformations alternatives and the objectives to fulfils are NFP such as reliability, availability and response time.
+The integration process is described in the following sections.
+
+%In this paper we propose a generic method to automate the search of optimal architectures (which fulfil at best the NFP of the system) from the design space.
+To represent the design space (set of architecture alternatives) we use model transformations compositions.
+The exploration step is done by using the NSGA-II algorithm.
+
+\subsubsection{\textbf{Genome representation}}
 
@@
 
-The first step of our work consists in applying the definition of the multi-objective optimization problem on our architecture design problem.
-Where the population to optimize or the design space represent a set of architecture alternatives and the objectives functions are $f_{1}:$ reliability, $f_{2}:$ availability and $f_{3}:$ response time.
-The architecture alternatives are formalized in a way that allow their reuse in different projects or products.
-To do so, we use model transformations mechanisms.
-An issue in using such methods is their complexity : how to identify which elements of the input architecture model transformation alternatives can be applied.
-To ease the development and maintenance of such model transformations, we propose to use a rule-based transformation languages and composition mechanisms.
+The major element to define in a multiple-objective optimization problem (MOOP) is the population to optimize.
+In our work, the population is a set of model transformations alternatives (MTA).
+Where each genome is a MTA and each gene represent the composition of this MTA.
 
-In our approach we have several Transformation Rules Alternatives (TRA).
-They represent the genomes to optimize in our multi-objective problem.
-Figure~\ref{genome} gives an overview of these genomes.
-Each genome $G_{i}, i \in {1,2,...,n}$ is composed of a set of TRA $(G = {TRA_{i}, i \in {1,2,...n}})$.
+Figure~\ref{genome} gives an overview of our mapping of a MOOP genome.
+A genome G represent a MTA and is composed of a sequences of genes.
+A gene is composed of a set of Transformation Rules Alternative (TRA).
+Each $TRA$ is, in turn, encoded as a pair $<Elements,Rule>$ where $Elements$ is a list of elements from the input model, and $Rule$ is a transformation rule which can be applied to $Elements$.
+
+%Each genome $G_{i}, i \in {1,2,...,n}$ is composed of a set of TRA $(G = {TRA_{i}, i \in {1,2,...n}})$.
 Each $TRA_{i}$ is, in turn, encoded as a pair $TRA_{i} = <Elements_{i},Rule_{i}>$ where $Elements_{i} (i ={1,2,...,n})$ is a list of elements from the input model, and $Rule_{i} (i ={1,2,...,n})$ is a transformation rule which can be applied to $Elements_{i}$.
 
-\subsection{Fitness evaluation of each genome}
+\subsubsection{\textbf{Fitness evaluation of each genome}}
 In each generation, the fitness of every genome in the population is evaluated.
@@
 
-\subsection{Genetic operators definition}
+\subsubsection{\textbf{Genetic operators}}
 In NSGA-II, in each iteration, the N genomes selected from the previous generation are used to create new N genomes using genetic operators.
@@
 
-\subsubsection{\textbf{Binary tournament selection}}
+\textbf{Binary tournament selection :} 
 This operation consists of choosing some genomes at random in the population, and selecting the fittest two for reproduction.
 The selection criteria are the rank of the containing front and the crowding distance for solutions within the same front.
-Several tournaments are run to produce the N needed genomes.
+Several tournaments are run to produce the needed genomes.
 
@@
 Figure~\ref{binary} illustrates this operation.
-On this figure, we suppose we have four genomes G1,G2,G3 and G4 respectively composed of TRA11,TRA21,TRA31 and TRA41.
-We apply two tournaments between paired genomes to produce the needed genomes.
-In the first round we have two tournaments between two different pairs of genomes (G1 with G2 and G3 with G4).
-In the second round we apply another tournament on the victorious genomes in the previous round (G2 and G4) .
+On this figure, we suppose we have four model transformations alternatives (genomes) MTA1, MTA2, MTA3 and MTA4 respectively composed of the following genes TRA11, TRA21, TRA31 and TRA41.
+We apply two tournaments between paired MTAs to produce the needed MTAs.
+In the first round we have two tournaments between two different pairs of MTAs (MTA1 with MTA2 and MTA3 with MTA4).
+In the second round we apply another tournament on the victorious MTAs in the previous round (MTA2 and MTA4) to get the fittest MTA which will be put in the mating pool for reproduction (generate new MTAs).
+In Figure~\ref{binary} the fittest MTA which is expected to appear in the mating pool is MTA4.
 
-The final genomes of the competition will always be the fittest genomes in the population.
-The more successful the genome is in competition, the more often that genome is expected to appear in the mating pool (In Figure~\ref{binary} the fittest genome is G4).
-
-\subsubsection{\textbf{Crossover}}
+\textbf{Crossover :} 
 The crossover consists of producing new genomes from the existing ones.
 When two genomes are selected using the binary tournament selection, two offspring solutions are created, with a given crossover probability, by exchanging parts of the parent genomes.
-This consists in randomly selecting a cut point in the genome vector, and all the target fragments beyond that point in either parent are swapped between the two parents.
+This consists in randomly selecting a cut point in the genome, and all the genes beyond that point in either parent are swapped between the two parents.
 
@@
 
-Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes G1 and G2 respectively composed of \{TRA11,TRA12,TRA13\} and \{TRA21,TRA22,TRA23\} to produce a new genome G3.
-As can be seen in Figure~\ref{crossover}, this operator combines TRA11 from G1 and {TRA22,TRA23} from G2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.
+Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes MTA1 and MTA2 respectively composed of the following genes \{TRA11,TRA12,TRA13\} and \{TRA21,TRA22,TRA23\} to produce a new genome MTA3 composed of new sequence \{TRA11,TRA22,TRA23\}.
+As can be seen in Figure~\ref{crossover}, this operator combines TRA11 from MTA1 and {TRA22,TRA23} from MTA2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.
 
-\subsubsection{\textbf{Mutation}}
+\textbf{Mutation :}
 After performing the crossover, the obtained solutions could be mutated with a given mutation probability.
@@
 
-The mutation operator act on a single genome G1 to obtained a muted genome G11 acts as follows.
+The mutation operator act on a single genome MTA1 to obtained a muted genome MTA11 acts as follows.
 The mutation operator selects a gene at random in the genome and changes its value.
-In Figure~\ref{mutation}, the third tile TRA13 is selected to mutate into TRA14 : we apply a different rule (i.e.
+In Figure~\ref{mutation}, the third gene TRA13 is selected to mutate into a new gene TRA14 : we apply a different rule (i.e.
 rule4) to the set of selected elements.
+
+The final step of our approach consists in using the NSGA-II algorithm described in Section~\ref{nsgaii} to our optimization design problem defined above to find the set of non-dominated model transformations alternatives.
 

### 2014-10-30 SysCon_article/article_syscon.tex
modification of all the paper

@@
 \label{Adapting}
-
 The next step of our approach consist in using model transformations definitions described in Section~\ref{transfos} and integrate them into a multiple-objectives optimization problem.
@@
 The integration process is described in the following sections.
-
-%In this paper we propose a generic method to automate the search of optimal architectures (which fulfil at best the NFP of the system) from the design space.
-To represent the design space (set of architecture alternatives) we use model transformations compositions.
-The exploration step is done by using the NSGA-II algorithm.
-
 \subsubsection{\textbf{Genome representation}}
@@
 \section{Acknowledgment}
-This research work has been carried out under the leadership of the Technological Research Institute SystemX, and therefore granted with public funds within the scope of the French Program "Investissements d’Avenir".
+This research work has been carried out under the leadership of the Technological Research Institute SystemX, and therefore granted with public funds within the scope of the French Program ``Investissements d'Avenir''.
 

### 2014-10-31 SysCon_article/article_syscon.tex
modifications of the paper

@@
 %% 2012/12/27
-%% by Smail Rahmoun
+%% by Smail Rahmounx
 
@@
 However, the design space produced by the composition of these model transformations is difficult to explore automatically.
-The main reason that make this exploration difficult is the size of the design space : the number of possible design choices grows exponentially with the number of model transformation alternatives.
+The main reason that makes this exploration difficult is the size of the design space: the number of possible design choices grows exponentially with the number of model transformation alternatives.
 This paper presents a MDA approach for design space exploration to deal with the ever-growing challenge of designing complex embedded systems.
@@
 \section{Introduction}
+
 Nowadays, modern systems become more and more large and complex and therefore more difficult to develop and maintain.
-For example, embedded critical systems which are often built to accomplish specific functionalities, can integrate several buses, software and hardware components.
-To guarantee properties such as safety, availability and robustness makes the design of these systems very challenging.
+For example, embedded critical systems such as avionic, railway and automotive are often built to guarantee the safety and robustness properties.
+To meet these challenging properties makes the design of embedded systems very complex.
 
 Model Driven Engineering (MDE) proposes the use of models as the key assets in the development of such systems.
-Model transformations approach become one of the basic building blocks of MDE.
-Even though MDE is being successfully applied in many scenarios, it still needs appropriate mechanisms to handle the development of complex, large-scale systems.
-One such mechanism is a facility to make transformations reusable, so that we can apply them to different contexts.
-In this work, we use generic model transformation to model design alternatives of the system.
-This process will help us to predict non-functional properties (NFP) of a system before its development\cite{1291833}.
+These models cover the whole system development cycle.
+They can be manipulated manually or automatically using model transformations.
+These transformations aims to enhance portability by way of separating system (abstract) architecture from platform (concrete) architecture.
+They facilitate the development of a system in abstraction, and simplifies implementation of that system across a variety of target platforms.
+In this work, we use model transformations to model design alternatives of the system.
+This process will help system architects to predict Non-Functional Properties (NFP) of a system before its development\cite{1291833}.
 This prediction can be exploited to drive decisions about which components should be used and how they should be connected so as to meet the NFP imposed on the design.
 
-Moreover, an issue in modeling a system is that, the NFP could conflict\footnote{improving one property can have a negative impact on other properties} with each other.
+%Even though MDE is being successfully applied in many scenarios, it still needs appropriate mechanisms to handle the development of complex, large-scale systems.
+One such mechanism is a facility to make transformations reusable, so that we can apply them to different contexts.
+
+Moreover, an issue in modeling a system is that, the NFP could conflict with each other: improving one property can have a negative impact on other properties.
 For example, improving the availability of a service is often done by replication of the service, which causes the increasing of the response time of these services\cite{Yu:2001:CLA:502059.502038}.
-Developing a system that satisfies at best all its NFP simultaneously is often not possible : improving a NFP of a system can deteriorate another NFP.
+Developing a system that satisfies at best all its NFP simultaneously is often not possible: improving a NFP of a system can deteriorate another NFP.
 As a consequence, system architects have to come up with several design alternatives and select the solutions which fulfils at best all NFP\cite{Coello98acomprehensive} simultaneously from all feasible alternatives.
-The selected solutions are called non-dominated solutions or Pareto optimal solutions : a solution x2 is non-dominated by another solution x1, if x2 matches or exceeds x1 in all objectives (NFP).
+The selected solutions are called non-dominated solutions or Pareto optimal solutions: a solution x2 is non-dominated by another solution x1, if x2 matches or exceeds x1 in all objectives (NFP).
 
 In order to obtain the set of Pareto optimal alternatives, some advanced multi-objective optimization evolutionary algorithms (MOEA) have been proposed.
-These algorithms apply some fitness evaluations and generic operators of variation.
-Thus, they are applicable to search spaces (e.g.
-design space) taking into account domain specific characteristics of the problem (e.g.
+These algorithms apply some fitness evaluations and generic operators.
+Thus, they are applicable to find solutions in complex design spaces taking into account domain specific characteristics of the problem (e.g.
 prediction of NFP).
-MOEA also provides selection operators which guide the search towards interesting regions of the search space by (i) favorizing non-dominated solutions; and (ii) finding a diverse set of solutions on the Pareto front..
+MOEA also provides selection operators which guide the search towards interesting regions of the search space by (i) favorizing non-dominated solutions; and (ii) finding a diverse set of solutions in the Pareto front : represents the set of possible solutions.
 
 In this paper, we introduce an approach, tailored for embedded system architecture design, where architecture alternatives are implemented as model transformations driven by NFPs.
-And to find good transformations alternatives that help system architects perform trade-off analysis, we use some advanced MOEA.
-More specific, we adapt (or map) model transformations mechanisms into a multiple-objective optimization problem.
+In order to select good transformations alternatives that help system architects perform trade-off analysis, we apply approaches based on MOEA.
+More specifically, we map model transformations mechanisms into a multiple-objective optimization problem.
 
@@
 Section~\ref{Problem} is dedicated to the problem statement.
-Section~\ref{Approach} gives an overview  of our approach.
-While Section~\ref{Adapting} details our approach.
+Section~\ref{MOEA} gives an overview of the current advanced MOEA.
+While Section~\ref{Approach} details the approach of this paper.
 Section~\ref{Related} presents the related work.
@@
 During the design of a safety-critical system, it is useful to model non functional properties (NFP), such as reliability, availability or temporal performances, already in early stages of the development process.
-Early NFP modeling enables the developer of the system to make design decision based on analyses and simulations.
-But, one major difficulty is that these NFP can be in conflict with each other, that is, improving one NFP can have a negative impact on others.
+Early NFP modeling enables system designers to make design decisions based on analyses and simulations.
+But, one major difficulty is that these NFP can be in conflict with each other, that is, improving one NFP can have a negative impact on some others.
 To construct a system that fulfils all its NFP simultaneously is often not possible.
@@
 Each pattern implements a well-known architectural solution which fulfils a set of NFP.
-To formalize these design patterns in a way that allows their reuse in different projects or products we implement them as model transformations.
+To formalize these design patterns in a way that allows their reuse in different projects or products we implement them as executable model transformations.
 
@@
 Moreover, using MOEA to deal with mode transformations alternatives can be challenging.
-We have (i) to generalize the architecture design problem as a multiple objective optimization problem; (ii) select the more suitable evolutionary algorithm to solve this optimization problem; and (iii) adapt the notions of model transformation techniques to this evolutionary algorithm.
+We have (i) to generalize the architecture design problem as a multiple objective optimization problem; (ii) select the more suitable evolutionary algorithm to solve this optimization problem; and (iii) map the notions of model transformation techniques to this evolutionary algorithm.
 
 \section{Multi-Objective Evolutionary Algorithm}
+\label{MOEA}
 
-An evolutionary algorithm (EA) is characterized by three features : (i) a set of solution candidates is maintained; (ii) a mating selection process is performed on this set, and (iii) several solutions may be combined in terms of recombination to generate new solutions.
+An evolutionary algorithm (EA) is characterized by three features: (i) a set of solution candidates is maintained; (ii) a mating selection process is performed on this set, and (iii) several solutions may be combined in terms of recombination to generate new solutions.
 
 The solution candidates are called \textbf{genomes} (or individuals) and the set of solution candidates is called the \textbf{population}.
-Each genome is composed of a sequence of genes and represents a possible solution to the problem at hand.
+Each genome is composed of a sequence of \textbf{genes} and represents a possible solution to the optimization problem.
 
 The mating selection process usually consists of two steps: \textbf{fitness evaluation} and \textbf{mating pool}.
-In the first step, the genomes are evaluated in the objective space and then assigned a scalar value called \textbf{fitness}, reflecting their quality.
-Afterwards, a mating pool is created by random sampling from the population according to the fitness values.
-For example using a binary tournament selection.
-Where two genomes are randomly chosen from the population, and the one with the better fitness value is copied to the mating pool.
+In the first step, the genomes are evaluated in the search space and then assigned a scalar value called \textbf{fitness}, reflecting their quality.
+Afterwards, a \textbf{mating pool} is created by random \textbf{sampling} from the population according to the fitness values.
+For example a common used sampling method is \textbf{binary tournament selection}.
+Here two genomes are randomly chosen from the population, and the one with the better fitness value is copied to the mating pool.
 This procedure is repeated until the mating pool is filled.
-
-Then, the variation operators are applied to the mating pool to obtain better solutions.
-Usually these operators are called \textbf{genetic operators}.
-With EAs, there are two operators namely the crossover (or recombination) and the mutation.
+Then, new solutions are produced by using \textbf{genetic operators}: crossover (or recombination) and mutation operators.
 
@@
 First, an initial population is created at random, which is the starting point of the evolution process.
-Then a loop consisting of the fitness evaluation, selection, genetic operators is executed a certain number of times.
+Then a loop consisting of the fitness evaluation and genetic operators is executed a certain number of times.
 Each loop iteration is called a generation, and often a predefined maximum number of generations serves as the termination criterion of the loop.
@@
 NSGA-II is an improved version of NSGA\cite{Srinivas94multiobjectiveoptimization} (Non-dominated sorting genetic algorithm).
-It inherited the non-dominance concept from NSGA and showed three innovations, (i) a crowding approach for diversity preservation; (ii) an elitism operator that helps in significantly speeding up the performance of the genetic algorithm (fast non-dominated sort); and (iii) an objective-wise distance computation.
+It inherited the non-dominance concept from NSGA and showed two main innovations: non-dominated ranking and crowding distance.
+Non-dominated ranking is a way to sort genomes in non-dominated fronts whereas crowding distance is a parameter that permits to preserve diversity among solutions of the same non-dominated front: a front represent a set of possible solutions.
 
@@
 
-Figure~\ref{nsgaii} gives an overview of how to use NSGA-II to automate the exploration of complex systems design space. The steps of this algorithm are as follow :
+Figure~\ref{nsgaii} gives an overview of how to use NSGA-II to automate the exploration of complex systems design space. As can be seen in the Figure, the algorithm is as follow :
 
 \begin{enumerate}
-\item Initially, Create a random parent population $P_{0}$ composed of N genomes (N = 3 in Figure~\ref{nsgaii}). N represent the size of the population.
-\item Sort the current population based on a non domination criterion (e.g. reliability, availability and response time).
-\item For each non-dominated solution, assign a fitness (rank) equal to its non-domination level (1 is the best level, 2 is the next best level, and so on).
-\item Create a child population $Q_{0}$ of size N using binary tournament selection, recombination, and mutation operators.
-\item From the first generation onwards, creation of each new generation constitutes the following steps :
-\item[5.a)] Create the mating pool $R_{t}$ of size 2N by combining the parent population $P_{t}$ and the child population $Q_{t}$.
-\item[5.b)] Sort the combined population $R_{t}$ according to the fast non-dominated sorting procedure to identify all non-dominated fronts $(F_{1} ,F_{2},...,F_{k})$.
-\item[5.c)] Generate the new parent population $P_{t}+1$ of size N by adding non-dominated solutions starting from the first ranked non-dominated front $F1$ and proceeding with the subsequently ranked non-dominated fronts $F_{1} ,F_{2}, .
+\item[\textbf{Step 1:}] Initially, Create a random parent population $P_{0}$ composed of N genomes (solutions candidates) (N = 3 in Figure~\ref{nsgaii}). N represents the size of the population.
+\item[\textbf{Step 2:}] Sort the current population based on a non domination criterion (e.g. reliability, availability and response time).
+\item[\textbf{Step 3:}] For each non-dominated solution, assign a fitness (rank) equal to its non-domination level (1 being the best level).
+\item[\textbf{Step 4:}] Create a child population $Q_{t}$ of size N using binary tournament selection and genetic operators.
+\item[\textbf{Step 5:}] From the current population, create new generations by following the next operations:
+\item[\textbf{Step 5.1:}] Create the mating pool $R_{t}$ of size 2*N by combining the parent population $P_{t}$ and the child population $Q_{t}$.
+\item[\textbf{Step 5.2:}] Sort the combined population $R_{t}$ according to the fast non-dominated sorting procedure\cite{Deb:2002:FEM:2221359.2221582} to identify all non-dominated fronts $(F_{1} ,F_{2},...,F_{k})$.
+Where each front represent a set of possible solutions.
+\item[\textbf{Step 5.3:}] Generate the new parent population $P_{t+1}$ of size N.
+The solutions belonging to the best non-dominated front, (i.e.
+$F_{1}$) represent the best solutions in $R_{t}$ and must be emphasized more than any other solution.
+If the size of $F_{1}$ is smaller than N, all solutions of $F_{1}$ are inserted in $P_{t+1}$.
+Then, the remaining population of $P_{t+1}$ is chosen from subsequent non-dominated fronts in order of their ranking: the solutions of $F_{2}$ are chosen next.
+However, as shown in Figure~\ref{nsgaii}, not all the solutions from $F_{2}$ can be inserted in population $P_{t+1}$.
+Indeed, the number of empty slots of $P_{t+1}$ is smaller than the number of fronts.
+In order to choose which ones will be selected, these solutions are sorted according to their crowding distance and, then, the number of best of them needed to fill the empty slots of $P_{t+1}$ are inserted and the others are rejected.
+\item[\textbf{Step 6:}] The created population $P_{t+1}$ is then used for selection, crossover and mutation (see Figure~\ref{nsgaii}) to create a new population $Q_{t+1}$, and so on for the next generations until a stopping criterion is met (e.g.
+maximum number of generations is reached).
+
+%starting from the first ranked non-dominated front $F1$ and proceeding with the subsequently ranked non-dominated fronts $F_{1} ,F_{2}, .
 .
@@
 This is achieved through a sorting process based on the crowding distance assigned to each solution contained in the $F_{k}th$ non-dominated front.
-Thus, the new parent population $P_{t}+1$ of size N is constructed.
-\item Perform the selection, crossover and mutation operations on the newly generated parent population $(P_{t}+1)$ to create the new child population $(Q_{t}+1)$) of size N (Figure~\ref{nsgaii}).
-\item Repeat Step 5 until a stopping criterion is met (e.g. maximum number of generations is reached).
-
+Thus, the new parent population $P_{t+1}$ of size N is constructed.
 \end{enumerate}
@@
 Figure~\ref{IS} graphically illustrates the approach proposed in this paper by showing the process underlying it.
-As can be seen in Figure~\ref{IS}, the process starts with an initial input software architecture which could be designed by software architects by using architecture design languages\cite{Medvidovic}.
+As can be seen in Figure~\ref{IS}, the process starts with an initial input software architecture which could be designed by some system architect by using architecture design languages.
 After that, the input model is transformed into a set of alternative architecture models (more detailed models) driven by a set of competing NFP.
@@
 The other reason of choosing AADL is to integrate our work in an existing framework RAMSES\footnote{Refinement of AADL Models for the Synthesis of Embdded Systems.
-\url{http://penelope.enst.fr/aadl/wiki/Projects}} which apply selection of design alternatives.
+\url{http://penelope.enst.fr/aadl/wiki/Projects}} which automate re-factoring of model transformations to apply design choices\cite{greg}.
 
@@
 In major cases, model transformations are grouped into two main categories of model transformation languages : (i) rule-based transformation languages, or (ii) imperative transformation languages\cite{Gorp06integratinga}.
-
-The first category express model transformation logics in a way that is easy to interpret and \textbf{adapt}.
-It permit to modify the pattern matching part of a transformation rule $TR$ which is sufficient to modify the set of elements this rule applies to.
+Rule-based transformation languages such as ATL (for ATLAS Transformation Language) are of great interest in our context since they express model transformation logics in a way that is easy to interpret and \textbf{adapt} into other methods (in this paper MOEA).
+It offers a number of rules that define the mapping from source (abstract architecture) elements to target (concrete architecture) elements.
 In contrary, the adaptation of imperative transformation languages are more difficult and requires a deep understanding of the control flow graph that leads to the execution of one or another transformation.
 
-We used in our work the first category of languages since it more easy to adapt into other methods (in this paper MOEA).
-Where model transformations are endogenous : the source and target models are the same.
-In our work we use a AADL to AADL model transformations in order to improve (or refine) the architecture of an embedded system while representing the result of this refinement in an analysable model.
-More specific, we use the rule-based transformation language ATL (for Atlas Transformation Language).
-
-A model transformation $MT$ is generally composed of a set of transformation rules $(TR_{i})$.
-Each transformation rule $TR_{i}$ is defined by a pair $<E_{j},R_{j}>$, where $E_{j}$ is the scope of the transformation rule $TR_{i}$ : the set of elements from the input model the transformation rule $TR_{i}$ can be applied to.
-And $R_{j}$ is the set of rules or actions which $TR_{i}$ executes when it is applied to an element of $E_{j}$ (i.e.
-creation of elements in the target model).
-
-%In the second step of this approach, we use the rule-based transformation language ATL (for Atlas Transformation Language), where architecture alternatives are implemented as model transformations driven by NFPs.
+In the application of a rule based transformation language, a model transformation $MT$ is generally composed of a set of transformation rules $(TR_{i})$.
+Each transformation rule $TR_{i}$ is defined by a pair $<E_{j},R_{j}>$.
+Where $E_{j}$ is the scope of the transformation rule $TR_{i}$.
+And $R_{j}$ is the set of rules or actions which $TR_{i}$ executes.
+The scope of each transformation rule is defined by pattern matching semantics : a transformation rule $TR$ is applied to every element in the model that matches a boolean expression (e.g.
+the boolean expression ``from" in the ATL language).
+Then, actions consists of a declarative creation and configuration of elements in the output model.
 
@@
 \label{Adapting}
-The next step of our approach consist in using model transformations definitions described in Section~\ref{transfos} and integrate them into a multiple-objectives optimization problem.
+The next step of our approach consist in using model transformations compositions described in Section~\ref{transfos} and integrate them into a multiple-objectives optimization problem (MOOP).
 Where the population to optimize or the design space represent a set of model transformations alternatives and the objectives to fulfils are NFP such as reliability, availability and response time.
 The integration process is described in the following sections.
+
 \subsubsection{\textbf{Genome representation}}
-
 \begin{figure}[!ht]
@@
 
-The major element to define in a multiple-objective optimization problem (MOOP) is the population to optimize.
-In our work, the population is a set of model transformations alternatives (MTA).
-Where each genome is a MTA and each gene represent the composition of this MTA.
+The first step in a MOOP is to define the population to optimize.
+In our work, this population represents a set of model transformations alternatives (MTA).
+Where each genome is a MTA and each gene represent the component of this MTA.
 
@@
 Each $TRA$ is, in turn, encoded as a pair $<Elements,Rule>$ where $Elements$ is a list of elements from the input model, and $Rule$ is a transformation rule which can be applied to $Elements$.
-
-%Each genome $G_{i}, i \in {1,2,...,n}$ is composed of a set of TRA $(G = {TRA_{i}, i \in {1,2,...n}})$.
-Each $TRA_{i}$ is, in turn, encoded as a pair $TRA_{i} = <Elements_{i},Rule_{i}>$ where $Elements_{i} (i ={1,2,...,n})$ is a list of elements from the input model, and $Rule_{i} (i ={1,2,...,n})$ is a transformation rule which can be applied to $Elements_{i}$.
+To be mentioned that, the sequence of transformation rules alternatives is ordered.
+A TRA exists only when a different rule may be applied to the same set of elements: $\exists \; i,j \; (Elements_{i} \cap Elements_{j} \neq \emptyset)$ encodes the existence of transformation rules alternatives $TRA_{i}$ or $TRA_{j}$.
 
@@
 The fitness is usually the value of the objective function in the optimization problem being solved.
-We defined in our work one fitness function corresponding to three objectives reliability, availability and response time.
+In our work, one fitness function corresponding to three objectives reliability, availability and response time.
 The aim of our work is to maximize these three objectives.
-
-The more fit genomes are stochastically selected from the current population, and each genome is modified (recombined and possibly randomly mutated) to form a new generation.
+In NSGA-II, the more fit genomes are stochastically selected from the current population, and each genome is modified (recombined and possibly randomly mutated) to form a new generation.
 
@@
 In NSGA-II, in each iteration, the N genomes selected from the previous generation are used to create new N genomes using genetic operators.
-This improves the existing solutions by mixing their genetic material (crossover) and/or by creating new material (mutation).
+This improves the existing solutions by mixing their genetic compositions (crossover) and/or by creating new compositions (mutation).
 Before applying the operators, the solutions are selected according to their fitness values, see Figure~\ref{nsgaii}.
@@
 On this figure, we suppose we have four model transformations alternatives (genomes) MTA1, MTA2, MTA3 and MTA4 respectively composed of the following genes TRA11, TRA21, TRA31 and TRA41.
-We apply two tournaments between paired MTAs to produce the needed MTAs.
+Each TRA is applied to the same set of elements $Elements_{1}$.
+We apply two tournaments between paired MTAs to produce the best MTA to apply to $Elements_{1}$.
 In the first round we have two tournaments between two different pairs of MTAs (MTA1 with MTA2 and MTA3 with MTA4).
@@
 \textbf{Crossover :} 
-The crossover consists of producing new genomes from the existing ones.
+The crossover consists in producing new genomes from the existing ones.
 When two genomes are selected using the binary tournament selection, two offspring solutions are created, with a given crossover probability, by exchanging parts of the parent genomes.
@@
 
-Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes MTA1 and MTA2 respectively composed of the following genes \{TRA11,TRA12,TRA13\} and \{TRA21,TRA22,TRA23\} to produce a new genome MTA3 composed of new sequence \{TRA11,TRA22,TRA23\}.
-As can be seen in Figure~\ref{crossover}, this operator combines TRA11 from MTA1 and {TRA22,TRA23} from MTA2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.
+Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes MTA1 and MTA2 respectively composed of the following genes \{TRA11,TRA12,TRA13\} and \{TRA21,TRA22,TRA23\} to produce new genomes MTA12 and MTA21, respectively composed of new sequences \{TRA21,TRA12,TRA13\} and \{TRA11,TRA22,TRA23\}.
+This operator combines MTA1 and MTA2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.
 
@@
 
-The mutation operator act on a single genome MTA1 to obtained a muted genome MTA11 acts as follows.
+The mutation operator acts on a single genome MTA1 to obtained a muted genome MTA11 acts as follows.
 The mutation operator selects a gene at random in the genome and changes its value.
@@
 
-The final step of our approach consists in using the NSGA-II algorithm described in Section~\ref{nsgaii} to our optimization design problem defined above to find the set of non-dominated model transformations alternatives.
+The final step of our approach consists in using the NSGA-II algorithm described in Section~\ref{MOEA} to our optimization design problem defined above to find the set of non-dominated model transformations alternatives.
 
@@
 Recently, some works have focused on the definition of model transformation alternatives.
-The first works introduced the superimposition mechanism\cite{Navarro:2011:UMT:2041790.2041840} to implement transformations alternatives.
-Another work\cite{Kavimandan:2011:MQS:2000259.2000264} proposed to implement transformations alternatives by using rule-based transformation languages.
-These works has been continued in\cite{Drago:2011} in order to deal with architecture quality problems.
+The first works introduced the superimposition mechanism\cite{Navarro:2011:UMT:2041790.2041840} in order to to implement transformations alternatives by replacing parts of a rule-based model transformation.
+Implementing alternatives while reusing rules was also an important challenge studied in \cite{Kavimandan:2011:MQS:2000259.2000264}.
 
-Our contribution is based on this work since it enable the factorization and composition of model transformations.
-However, this approach doesn't propose any algorithm to select the non-dominated (or pareto) model transformations alternatives which fulfil at best a set of competing non-functional properties.
+These works are the building blocks of other works, such in\cite{Drago:2011} where they performed model transformations factorizations and compositions in order to implement quality driven model transformation alternatives : specification of some variants in the source code of model transformations in order to produce output models having different quality attributes.
+
+In \cite{greg} the authors implement a framework that improve system architectures by using a semi-automatic selection and specialization of model transformation alternatives while taking care of transformation dependenciess.
+
+Our contribution is based on these work since they enable the factorization and composition of model transformations.
+However, these approaches don't propose any algorithm to select the non-dominated (or pareto) model transformations alternatives which fulfil at best a set of competing non-functional properties.
 
 \subsection{multi-objective metaheuristic optimization}
+
+For the optimization of NFP, the first works consisted at using a cyclic process\cite{Bosch99softwarearchitecture}.
+The benefit of this process is its simplicity.
+The process can be tailored to different non-functional properties by using specific evaluation methods and architecture transformations.
+But this process focuses on only one non-functional property at a time.
+Unlike in our work, we take into account several properties at a same time (e.g.
+reliability, availability and response time).
+
 Aleti et al.\cite{Gr5069138} have developed the ArchOpteryx framework.
@@
 
-Compared to DesignBots\cite{Diaz-Pace:2007:UPT:1784860.1784865}, in our method model transformations are not decomposed into subplans, each transformation is performed atomically.
-
-For the optimization of NFP another work consists at using a cyclic process\cite{Bosch99softwarearchitecture}.
-The benefit of this process is its simplicity.
-The process can be tailored to different non-functional properties by using specific evaluation methods and architecture transformations.
-But this process focuses on only one non-functional property at a time unlike us who take into account several properties at a same time (e.g.
-reliability, availability and response time).
-
 \section{Conclusion}
 \label{Conclu}
-An architecture design method has been presented that explicitly addresses the NFP put on the architecture.
-The proposed approach aims at improving system architecture models using two mechanisms.
-On the one hand, model transformations compositions to formalize model design alternatives.
-On the other hand, an elitist multiple-objective optimisation algorithm to explore this design space.
+%The main contribution of the paper is to bring together Non-functional Properties to design decisions (represented as model transformations) and to use this information to automate the selection of architectural refinements based on these relationships.
+
+In this paper we propose an approach which aims at improving system architecture models using two mechanisms: (ii) using model transformations compositions to formalize model design alternatives; and (ii) mapping these model transformations to an elitist multiple-objective optimisation algorithm to explore the design space.
 
@@
 
-In the future, we plan to integrate our approach in the framework RAMSES and evaluating our approach in more details quantitatively (i.e. experimenting it on a an industrial case study)\cite{greg}.
+In the future, we plan to integrate our approach in the framework RAMSES and evaluating our approach in more details quantitatively (i.e.
+experimenting it on a an industrial case study)\cite{pautet:Cadoret2013}.
 
@@
 
+\bibitem{pautet:Cadoret2013}
+F.~{Cadoret}, T.~{Robert}, E.~{Borde}, L.~{Pautet}, and F.~{Singhoff},
+  ``Deterministic implementation of periodic-delayed communications and
+  experimentation in aadl,'' Paderborn, Allemagne, June 2013.
+ \begin{quotation}\noindent category=inproceedings language=en audience=2
+  state=toappear project=safir dept=infres group=s3 id=13716 \end{quotation}
+
 \bibitem{Coello98acomprehensive}
@@
   Wiley \&amp; Sons, Inc., 2001.
-
-\bibitem{Diaz-Pace:2007:UPT:1784860.1784865}
-J.~A. D\'{\i}az-Pace and M.~R. Campo, ``Using planning techniques to assist
-  quality-driven architectural design exploration,'' in \emph{Proceedings of
-  the Quality of Software Architectures 3rd International Conference on
-  Software Architectures, Components, and Applications}, ser. QoSA'07.\hskip
-  1em plus 0.5em minus 0.4em\relax Berlin, Heidelberg: Springer-Verlag, 2007,
-  pp. 33--52. [Online]. Available:
-  \url{http://dl.acm.org/citation.cfm?id=1784860.1784865}
 
@@
 
-\bibitem{Medvidovic}
-N.~Medvidovic and R.~N. Taylor, ``A classification and comparison framework for
-  software architecture description languages,'' \emph{IEEE Trans. Softw.
-  Eng.}, vol.~26, no.~1, pp. 70--93, Jan. 2000. [Online]. Available:
-  \url{http://dx.doi.org/10.1109/32.825767}
+%\bibitem{Medvidovic}
+%N.~Medvidovic and R.~N. Taylor, ``A classification and comparison framework for
+%  software architecture description languages,'' \emph{IEEE Trans. Softw.
+%%  Eng.}, vol.~26, no.~1, pp. 70--93, Jan. 2000. [Online]. Available:
+%  \url{http://dx.doi.org/10.1109/32.825767}
 

### 2014-11-05 SysCon_article/article_syscon.tex
suppresion of LaTex warnings

@@
 The main reason that makes this exploration difficult is the size of the design space: the number of possible design choices grows exponentially with the number of model transformation alternatives.
-This paper presents a MDA approach for design space exploration to deal with the ever-growing challenge of designing complex embedded systems.
+This paper presents a Model Driven Engineering approach for design space exploration to deal with the ever-growing challenge of designing complex embedded systems.
 This approach allows the system architects to automatically select the most adequate model transformations compositions by using multi-objectives optimization evolutionary algorithms.
@@
 \section{Introduction}
-
 Nowadays, modern systems become more and more large and complex and therefore more difficult to develop and maintain.
@@
 They facilitate the development of a system in abstraction, and simplifies implementation of that system across a variety of target platforms.
-In this work, we use model transformations to model design alternatives of the system.
+In this work, we use model transformations to model the system design alternatives.
 This process will help system architects to predict Non-Functional Properties (NFP) of a system before its development\cite{1291833}.
 This prediction can be exploited to drive decisions about which components should be used and how they should be connected so as to meet the NFP imposed on the design.
-
-%Even though MDE is being successfully applied in many scenarios, it still needs appropriate mechanisms to handle the development of complex, large-scale systems.
-One such mechanism is a facility to make transformations reusable, so that we can apply them to different contexts.
 
@@
 
-\subsection{Mapping model transformation alternatives into a multiple-objectives optimization problem}
+\subsection{Mapping model transformation alternatives into a multiple objectives optimization problem}
 \label{Adapting}
@@
 
-Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes MTA1 and MTA2 respectively composed of the following genes \{TRA11,TRA12,TRA13\} and \{TRA21,TRA22,TRA23\} to produce new genomes MTA12 and MTA21, respectively composed of new sequences \{TRA21,TRA12,TRA13\} and \{TRA11,TRA22,TRA23\}.
+Figure~\ref{crossover} illustrates the result of applying the crossover operator to two parent genomes MTA1 and MTA2 respectively composed of the following genes \{TRA11, TRA12, TRA13\} and \{TRA21, TRA22, TRA23\} to produce new genomes MTA12 and MTA21, respectively composed of new sequences \{TRA21,TRA12,TRA13\} and \{TRA11,TRA22,TRA23\}.
 This operator combines MTA1 and MTA2 by selecting a single point on the genome and swapping the genes between the two genomes that lie beyond this point.

### 2014-11-06 launchers/fr.tpt.aadl.ramses.control.support.workflow.edit/src/fr/tpt/aadl/ramses/control/workflow/provider/AnalysisSequenceItemProvider.java
first incomplete implementation of the mcda-based merge of model transformations

@@ -46,12 +46,6 @@ import fr.tpt.aadl.ramses.control.workflow.WorkflowPackage ;
  */
 public class AnalysisSequenceItemProvider
   extends AbstractAnalysisItemProvider
-  implements
-    IEditingDomainItemProvider,
-    IStructuredItemContentProvider,
-    ITreeItemContentProvider,
-    IItemLabelProvider,
-    IItemPropertySource
 {
   /**
    * This constructs an instance from a factory and a notifier.

### 2014-11-06 launchers/fr.tpt.aadl.ramses.control.support.workflow.edit/src/fr/tpt/aadl/ramses/control/workflow/provider/ConjunctionItemProvider.java

@@ -42,12 +42,6 @@ import fr.tpt.aadl.ramses.control.workflow.WorkflowPackage ;
  */
 public class ConjunctionItemProvider
   extends AnalysisSequenceItemProvider
-  implements
-    IEditingDomainItemProvider,
-    IStructuredItemContentProvider,
-    ITreeItemContentProvider,
-    IItemLabelProvider,
-    IItemPropertySource
 {
   /**
    * This constructs an instance from a factory and a notifier.

### 2014-11-06 launchers/fr.tpt.aadl.ramses.control.support.workflow.edit/src/fr/tpt/aadl/ramses/control/workflow/provider/DisjunctionItemProvider.java

@@ -42,12 +42,6 @@ import fr.tpt.aadl.ramses.control.workflow.WorkflowPackage ;
  */
 public class DisjunctionItemProvider
   extends AnalysisSequenceItemProvider
-  implements
-    IEditingDomainItemProvider,
-    IStructuredItemContentProvider,
-    ITreeItemContentProvider,
-    IItemLabelProvider,
-    IItemPropertySource
 {
   /**
    * This constructs an instance from a factory and a notifier.

### 2014-11-06 launchers/fr.tpt.aadl.ramses.control.support.workflow.edit/src/fr/tpt/aadl/ramses/control/workflow/provider/GenerationItemProvider.java

@@ -40,12 +40,6 @@ import org.eclipse.emf.edit.provider.ITreeItemContentProvider ;
  */
 public class GenerationItemProvider
   extends WorkflowElementItemProvider
-  implements
-    IEditingDomainItemProvider,
-    IStructuredItemContentProvider,
-    ITreeItemContentProvider,
-    IItemLabelProvider,
-    IItemPropertySource
 {
   /**
    * This constructs an instance from a factory and a notifier.

### 2014-11-06 launchers/fr.tpt.aadl.ramses.control.support.workflow.edit/src/fr/tpt/aadl/ramses/control/workflow/provider/LoopItemProvider.java

@@ -49,12 +49,6 @@ import fr.tpt.aadl.ramses.control.workflow.WorkflowPackage ;
  */
 public class LoopItemProvider
   extends WorkflowElementItemProvider
-  implements
-    IEditingDomainItemProvider,
-    IStructuredItemContentProvider,
-    ITreeItemContentProvider,
-    IItemLabelProvider,
-    IItemPropertySource
 {
   /**
    * This constructs an instance from a factory and a notifier.

### 2014-11-06 launchers/fr.tpt.aadl.ramses.control.support.workflow.edit/src/fr/tpt/aadl/ramses/control/workflow/provider/UnparseItemProvider.java

@@ -46,12 +46,6 @@ import fr.tpt.aadl.ramses.control.workflow.WorkflowPackage ;
  */
 public class UnparseItemProvider
   extends WorkflowElementItemProvider
-  implements
-    IEditingDomainItemProvider,
-    IStructuredItemContentProvider,
-    ITreeItemContentProvider,
-    IItemLabelProvider,
-    IItemPropertySource
 {
   /**
    * This constructs an instance from a factory and a notifier.

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.manual/src/fr/tpt/aadl/ramses/transformation/selection/manual/ManualSelection.java

@@ -45,6 +45,7 @@ import fr.tpt.aadl.ramses.transformation.selection.IHM.IHM ;
 import fr.tpt.aadl.ramses.transformation.launcher.ArchitectureRefinementProcessLauncher ;
 import fr.tpt.aadl.ramses.transformation.selection.ITransformationSelection ;
 import fr.tpt.aadl.ramses.transformation.selection.RuleApplicationUtils ;
+import fr.tpt.aadl.ramses.transformation.selection.TransformationRuleAlternative ;
 import fr.tpt.aadl.ramses.transformation.selection.TupleEntry ;
 import fr.tpt.aadl.ramses.transformation.tip.ElementTransformation ;
 import fr.tpt.aadl.ramses.transformation.trc.Transformation ;
@@ -305,7 +306,10 @@ public class ManualSelection implements ITransformationSelection,LoopManager {
 	        				Map.Entry<List<EObject>, ArrayList<String>> tuple = GlobalVariables.testMap.entrySet().iterator().next();
 	        				if( GlobalVariables.tuplesToApply.get(i).Rules.size()>1){
 		        				try{	 
-			        					RuleApplicationUtils.setTransformationToApply(tuple, GlobalVariables.tuplesToApply.get(i).getChoosenRule(), GlobalVariables.applytuple);
+		        				  TransformationRuleAlternative tra = new TransformationRuleAlternative(tuple.getKey(), 
+		        	                                                                              tuple.getValue());
+		        	        
+			        					RuleApplicationUtils.setTransformationToApply(tra, GlobalVariables.tuplesToApply.get(i).getChoosenRule(), GlobalVariables.applytuple);
 			        					//System.out.println("setTransformationToApply is succefully set !");
 			        				}
 			        				catch(Exception e){

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/dependency/graph/graph/DependencyArc.java

@@ -1,0 +1,78 @@
+/**
+ */
+package fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph;
+
+import org.eclipse.emf.ecore.EObject;
+
+/**
+ * <!-- begin-user-doc -->
+ * A representation of the model object '<em><b>Dependency Arc</b></em>'.
+ * <!-- end-user-doc -->
+ *
+ * <p>
+ * The following features are supported:
+ * <ul>
+ *   <li>{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyArc#getSourceNode <em>Source Node</em>}</li>
+ *   <li>{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyArc#getTargetNode <em>Target Node</em>}</li>
+ * </ul>
+ * </p>
+ *
+ * @see fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphPackage#getDependencyArc()
+ * @model
+ * @generated
+ */
+public interface DependencyArc extends EObject
+{
+  /**
+   * Returns the value of the '<em><b>Source Node</b></em>' reference.
+   * <!-- begin-user-doc -->
+   * <p>
+   * If the meaning of the '<em>Source Node</em>' reference isn't clear,
+   * there really should be more of a description here...
+   * </p>
+   * <!-- end-user-doc -->
+   * @return the value of the '<em>Source Node</em>' reference.
+   * @see #setSourceNode(DependencyNode)
+   * @see fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphPackage#getDependencyArc_SourceNode()
+   * @model required="true"
+   * @generated
+   */
+  DependencyNode getSourceNode();
+
+  /**
+   * Sets the value of the '{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyArc#getSourceNode <em>Source Node</em>}' reference.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @param value the new value of the '<em>Source Node</em>' reference.
+   * @see #getSourceNode()
+   * @generated
+   */
+  void setSourceNode(DependencyNode value);
+
+  /**
+   * Returns the value of the '<em><b>Target Node</b></em>' reference.
+   * <!-- begin-user-doc -->
+   * <p>
+   * If the meaning of the '<em>Target Node</em>' reference isn't clear,
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/dependency/graph/graph/DependencyGraph.java

@@ -1,0 +1,43 @@
+/**
+ */
+package fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph;
+
+import org.eclipse.emf.common.util.EList;
+
+import org.eclipse.emf.ecore.EObject;
+
+/**
+ * <!-- begin-user-doc -->
+ * A representation of the model object '<em><b>Dependency Graph</b></em>'.
+ * <!-- end-user-doc -->
+ *
+ * <p>
+ * The following features are supported:
+ * <ul>
+ *   <li>{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyGraph#getNodes <em>Nodes</em>}</li>
+ * </ul>
+ * </p>
+ *
+ * @see fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphPackage#getDependencyGraph()
+ * @model
+ * @generated
+ */
+public interface DependencyGraph extends EObject
+{
+  /**
+   * Returns the value of the '<em><b>Nodes</b></em>' containment reference list.
+   * The list contents are of type {@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyNode}.
+   * <!-- begin-user-doc -->
+   * <p>
+   * If the meaning of the '<em>Nodes</em>' containment reference list isn't clear,
+   * there really should be more of a description here...
+   * </p>
+   * <!-- end-user-doc -->
+   * @return the value of the '<em>Nodes</em>' containment reference list.
+   * @see fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphPackage#getDependencyGraph_Nodes()
+   * @model containment="true"
+   * @generated
+   */
+  EList<DependencyNode> getNodes();
+
+} // DependencyGraph

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/dependency/graph/graph/DependencyNode.java

@@ -1,0 +1,77 @@
+/**
+ */
+package fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph;
+
+import org.eclipse.emf.common.util.EList;
+
+import org.eclipse.emf.ecore.EObject;
+
+/**
+ * <!-- begin-user-doc -->
+ * A representation of the model object '<em><b>Dependency Node</b></em>'.
+ * <!-- end-user-doc -->
+ *
+ * <p>
+ * The following features are supported:
+ * <ul>
+ *   <li>{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyNode#getOutArcs <em>Out Arcs</em>}</li>
+ *   <li>{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyNode#getInArcs <em>In Arcs</em>}</li>
+ *   <li>{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyNode#getMatchedElements <em>Matched Elements</em>}</li>
+ * </ul>
+ * </p>
+ *
+ * @see fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphPackage#getDependencyNode()
+ * @model
+ * @generated
+ */
+public interface DependencyNode extends EObject
+{
+  /**
+   * Returns the value of the '<em><b>Out Arcs</b></em>' containment reference list.
+   * The list contents are of type {@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyArc}.
+   * <!-- begin-user-doc -->
+   * <p>
+   * If the meaning of the '<em>Out Arcs</em>' containment reference list isn't clear,
+   * there really should be more of a description here...
+   * </p>
+   * <!-- end-user-doc -->
+   * @return the value of the '<em>Out Arcs</em>' containment reference list.
+   * @see fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphPackage#getDependencyNode_OutArcs()
+   * @model containment="true"
+   * @generated
+   */
+  EList<DependencyArc> getOutArcs();
+
+  /**
+   * Returns the value of the '<em><b>In Arcs</b></em>' reference list.
+   * The list contents are of type {@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyArc}.
+   * <!-- begin-user-doc -->
+   * <p>
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/dependency/graph/graph/GraphPackage.java

@@ -1,0 +1,398 @@
+/**
+ */
+package fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph;
+
+import org.eclipse.emf.ecore.EClass;
+import org.eclipse.emf.ecore.EPackage;
+import org.eclipse.emf.ecore.EReference;
+
+/**
+ * <!-- begin-user-doc -->
+ * The <b>Package</b> for the model.
+ * It contains accessors for the meta objects to represent
+ * <ul>
+ *   <li>each class,</li>
+ *   <li>each feature of each class,</li>
+ *   <li>each operation of each class,</li>
+ *   <li>each enum,</li>
+ *   <li>and each data type</li>
+ * </ul>
+ * <!-- end-user-doc -->
+ * @see fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphFactory
+ * @model kind="package"
+ * @generated
+ */
+public interface GraphPackage extends EPackage
+{
+  /**
+   * The package name.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  String eNAME = "graph";
+
+  /**
+   * The package namespace URI.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  String eNS_URI = "http://fr.tpt.aadl.ramses.transformation/DependencyGraph/1.0";
+
+  /**
+   * The package namespace name.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  String eNS_PREFIX = "fr.tpt.aadl.ramses.transformation.selection.dependency";
+
+  /**
+   * The singleton instance of the package.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  GraphPackage eINSTANCE = fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.impl.GraphPackageImpl.init();
+
+  /**
+   * The meta object id for the '{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.impl.DependencyGraphImpl <em>Dependency Graph</em>}' class.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @see fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.impl.DependencyGraphImpl
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/dependency/graph/graph/impl/DependencyNodeImpl.java

@@ -1,0 +1,241 @@
+/**
+ */
+package fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.impl;
+
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyArc;
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyNode;
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphPackage;
+
+import java.util.Collection;
+
+import org.eclipse.emf.common.notify.NotificationChain;
+
+import org.eclipse.emf.common.util.EList;
+
+import org.eclipse.emf.ecore.EClass;
+import org.eclipse.emf.ecore.EObject;
+import org.eclipse.emf.ecore.InternalEObject;
+
+import org.eclipse.emf.ecore.impl.MinimalEObjectImpl;
+
+import org.eclipse.emf.ecore.util.EObjectContainmentEList;
+import org.eclipse.emf.ecore.util.EObjectResolvingEList;
+import org.eclipse.emf.ecore.util.InternalEList;
+
+/**
+ * <!-- begin-user-doc -->
+ * An implementation of the model object '<em><b>Dependency Node</b></em>'.
+ * <!-- end-user-doc -->
+ * <p>
+ * The following features are implemented:
+ * <ul>
+ *   <li>{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.impl.DependencyNodeImpl#getOutArcs <em>Out Arcs</em>}</li>
+ *   <li>{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.impl.DependencyNodeImpl#getInArcs <em>In Arcs</em>}</li>
+ *   <li>{@link fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.impl.DependencyNodeImpl#getMatchedElements <em>Matched Elements</em>}</li>
+ * </ul>
+ * </p>
+ *
+ * @generated
+ */
+public class DependencyNodeImpl extends MinimalEObjectImpl.Container implements DependencyNode
+{
+  /**
+   * The cached value of the '{@link #getOutArcs() <em>Out Arcs</em>}' containment reference list.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @see #getOutArcs()
+   * @generated
+   * @ordered
+   */
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/dependency/graph/graph/impl/GraphPackageImpl.java

@@ -1,0 +1,289 @@
+/**
+ */
+package fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.impl;
+
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyArc;
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyGraph;
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyNode;
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphFactory;
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphPackage;
+
+import org.eclipse.emf.ecore.EClass;
+import org.eclipse.emf.ecore.EPackage;
+import org.eclipse.emf.ecore.EReference;
+
+import org.eclipse.emf.ecore.impl.EPackageImpl;
+
+/**
+ * <!-- begin-user-doc -->
+ * An implementation of the model <b>Package</b>.
+ * <!-- end-user-doc -->
+ * @generated
+ */
+public class GraphPackageImpl extends EPackageImpl implements GraphPackage
+{
+  /**
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  private EClass dependencyGraphEClass = null;
+
+  /**
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  private EClass dependencyNodeEClass = null;
+
+  /**
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  private EClass dependencyArcEClass = null;
+
+  /**
+   * Creates an instance of the model <b>Package</b>, registered with
+   * {@link org.eclipse.emf.ecore.EPackage.Registry EPackage.Registry} by the package
+   * package URI value.
+   * <p>Note: the correct way to create the package is via the static
+   * factory method {@link #init init()}, which also performs
+   * initialization of the package, or returns the registered package,
+   * if one already exists.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @see org.eclipse.emf.ecore.EPackage.Registry
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/dependency/graph/graph/util/DependencyGraphUtils.java

@@ -1,0 +1,148 @@
+package fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.util;
+
+import java.util.ArrayList ;
+import java.util.Iterator ;
+import java.util.List ;
+import java.util.Map ;
+import java.util.Map.Entry ;
+
+import org.eclipse.emf.ecore.EObject ;
+
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyArc ;
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyGraph ;
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyNode ;
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphFactory ;
+import fr.tpt.aadl.ramses.transformation.trc.TrcSpecification ;
+import fr.tpt.aadl.ramses.transformation.trc.util.TaggedRuleApplicationTulpe ;
+import fr.tpt.aadl.ramses.transformation.trc.util.TrcUtils ;
+
+public class DependencyGraphUtils
+{
+
+  public static DependencyGraph createDependencyGraph(
+      TrcSpecification trc,
+      Map<List<EObject>, ArrayList<String>> patternMatchingMap)
+  {
+    DependencyGraph result = GraphFactory.eINSTANCE.createDependencyGraph();
+    
+    Iterator<Entry<List<EObject>, ArrayList<String>>> patternMatchingIt = patternMatchingMap.entrySet().iterator();
+    
+    List<List<EObject>> treatedObjects = new ArrayList<List<EObject>>();
+    while (patternMatchingIt.hasNext()) 
+    {
+      Map.Entry<List<EObject>, ArrayList<String>> tuple = (Map.Entry<List<EObject>, ArrayList<String>>)patternMatchingIt.next();
+      List<EObject> currentElements = tuple.getKey();
+      List<String> currentTransformationAlternatives = tuple.getValue();
+      if(false == treatedObjects.contains(currentElements))
+        treatedObjects.add(currentElements);
+      else
+      {
+        DependencyNode dn = getOrCreateDependencyNode(result, currentElements);
+        
+        // Retrieve dependencies for each alternative
+        for(String ruleId: currentTransformationAlternatives)
+        {
+          List<List<TaggedRuleApplicationTulpe>> accessibleTupleList =
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/dependency/graph/graph/util/GraphAdapterFactory.java

@@ -1,0 +1,172 @@
+/**
+ */
+package fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.util;
+
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.*;
+
+import org.eclipse.emf.common.notify.Adapter;
+import org.eclipse.emf.common.notify.Notifier;
+
+import org.eclipse.emf.common.notify.impl.AdapterFactoryImpl;
+
+import org.eclipse.emf.ecore.EObject;
+
+/**
+ * <!-- begin-user-doc -->
+ * The <b>Adapter Factory</b> for the model.
+ * It provides an adapter <code>createXXX</code> method for each class of the model.
+ * <!-- end-user-doc -->
+ * @see fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphPackage
+ * @generated
+ */
+public class GraphAdapterFactory extends AdapterFactoryImpl
+{
+  /**
+   * The cached model package.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  protected static GraphPackage modelPackage;
+
+  /**
+   * Creates an instance of the adapter factory.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  public GraphAdapterFactory()
+  {
+    if (modelPackage == null)
+    {
+      modelPackage = GraphPackage.eINSTANCE;
+    }
+  }
+
+  /**
+   * Returns whether this factory is applicable for the type of the object.
+   * <!-- begin-user-doc -->
+   * This implementation returns <code>true</code> if the object is either the model's package or is an instance object of the model.
+   * <!-- end-user-doc -->
+   * @return whether this factory is applicable for the type of the object.
+   * @generated
+   */
+  @Override
+  public boolean isFactoryForType(Object object)
+  {
+    if (object == modelPackage)
+    {
+      return true;
+    }
+    if (object instanceof EObject)
+    {
+      return ((EObject)object).eClass().getEPackage() == modelPackage;
+    }
+    return false;
+  }
+
+  /**
+   * The switch that delegates to the <code>createXXX</code> methods.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  protected GraphSwitch<Adapter> modelSwitch =
+    new GraphSwitch<Adapter>()
+    {
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/dependency/graph/graph/util/GraphSwitch.java

@@ -1,0 +1,165 @@
+/**
+ */
+package fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.util;
+
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.*;
+
+import org.eclipse.emf.ecore.EObject;
+import org.eclipse.emf.ecore.EPackage;
+
+import org.eclipse.emf.ecore.util.Switch;
+
+/**
+ * <!-- begin-user-doc -->
+ * The <b>Switch</b> for the model's inheritance hierarchy.
+ * It supports the call {@link #doSwitch(EObject) doSwitch(object)}
+ * to invoke the <code>caseXXX</code> method for each class of the model,
+ * starting with the actual class of the object
+ * and proceeding up the inheritance hierarchy
+ * until a non-null result is returned,
+ * which is the result of the switch.
+ * <!-- end-user-doc -->
+ * @see fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.GraphPackage
+ * @generated
+ */
+public class GraphSwitch<T> extends Switch<T>
+{
+  /**
+   * The cached model package
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  protected static GraphPackage modelPackage;
+
+  /**
+   * Creates an instance of the switch.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @generated
+   */
+  public GraphSwitch()
+  {
+    if (modelPackage == null)
+    {
+      modelPackage = GraphPackage.eINSTANCE;
+    }
+  }
+
+  /**
+   * Checks whether this is a switch for the given package.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @parameter ePackage the package in question.
+   * @return whether this is a switch for the given package.
+   * @generated
+   */
+  @Override
+  protected boolean isSwitchFor(EPackage ePackage)
+  {
+    return ePackage == modelPackage;
+  }
+
+  /**
+   * Calls <code>caseXXX</code> for each class of the model until one returns a non null result; it yields that result.
+   * <!-- begin-user-doc -->
+   * <!-- end-user-doc -->
+   * @return the first non-null result returned by a <code>caseXXX</code> call.
+   * @generated
+   */
+  @Override
+  protected T doSwitch(int classifierID, EObject theEObject)
+  {
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/mcda/DependencyValidation.java

@@ -1,0 +1,90 @@
+package fr.tpt.aadl.ramses.transformation.selection.mcda;
+
+import java.util.List ;
+
+import org.eclipse.emf.ecore.EObject ;
+
+import fr.tpt.aadl.ramses.transformation.trc.TrcSpecification ;
+import fr.tpt.aadl.ramses.transformation.trc.util.RuleApplicationTulpe ;
+import fr.tpt.aadl.ramses.transformation.trc.util.TaggedRuleApplicationTulpe ;
+import fr.tpt.aadl.ramses.transformation.trc.util.TrcUtils ;
+
+public class DependencyValidation
+{
+
+  private TrcSpecification trc;
+  private List<RuleApplicationTulpe> ruleApplicationList ;
+  
+  public DependencyValidation(TrcSpecification trc,
+                              List<RuleApplicationTulpe> ruleApplicationList)
+  {
+    this.trc = trc;
+    this.ruleApplicationList = ruleApplicationList;
+  }
+
+  public boolean validate()
+  {
+    
+    for(RuleApplicationTulpe rat: ruleApplicationList)
+    {
+      List<List<TaggedRuleApplicationTulpe>> dependenciesDisjunctionList = 
+          TrcUtils.getNormalizedDependencies(trc,
+                                             rat.getPatternMatchedElement(),
+                                             rat.getTransformationRuleName());
+      if(dependenciesDisjunctionList.isEmpty())
+        continue;
+      
+      boolean isDisjunctionValid = false;
+      for(List<TaggedRuleApplicationTulpe> dependencyConjunctionList:
+        dependenciesDisjunctionList)
+      {
+        if(validateConjunction(dependencyConjunctionList))
+        {
+          isDisjunctionValid = true;
+          break;
+        }
+      }
+      
+      if(isDisjunctionValid==false)
+        return false;
+      
+    }
+    return true ;
+  }
+
+  private
+      boolean
+      validateConjunction(List<TaggedRuleApplicationTulpe> dependencyConjunctionList)
+  {
+    for(TaggedRuleApplicationTulpe trat: dependencyConjunctionList)
+    {
+      if(false==validateDependency(trat))
+        return false;
+    }
+    return true ;
+  }
+
+  private boolean validateDependency(TaggedRuleApplicationTulpe trat)
+  {
+    // check if trat is valid in ruleApplicationList
+    if(trat.isExclusion())
+      return !isInRuleApplicationList(trat);
+    else
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/mcda/MCDABasedTransformationSelection.java

@@ -1,0 +1,218 @@
+package fr.tpt.aadl.ramses.transformation.selection.mcda;
+
+import java.io.FileInputStream ;
+import java.io.IOException ;
+import java.io.InputStream ;
+import java.util.ArrayList ;
+import java.util.HashMap ;
+import java.util.Iterator ;
+import java.util.LinkedHashMap ;
+import java.util.List ;
+import java.util.Map ;
+import java.util.Properties ;
+import java.util.Map.Entry ;
+
+import org.apache.log4j.Logger ;
+import org.eclipse.core.runtime.IProgressMonitor ;
+import org.eclipse.emf.ecore.EObject ;
+import org.eclipse.emf.ecore.resource.Resource ;
+import org.eclipse.emf.ecore.resource.ResourceSet ;
+import org.osate.aadl2.instance.SystemInstance ;
+import org.osate.aadl2.modelsupport.errorreporting.AnalysisErrorReporterManager ;
+
+import fr.tpt.aadl.ramses.control.support.analysis.AnalysisException ;
+import fr.tpt.aadl.ramses.control.support.config.ConfigurationException ;
+import fr.tpt.aadl.ramses.control.support.config.RamsesConfiguration ;
+import fr.tpt.aadl.ramses.control.support.generator.TransformationException ;
+import fr.tpt.aadl.ramses.control.support.instantiation.ParseException ;
+import fr.tpt.aadl.ramses.control.support.utils.Names ;
+import fr.tpt.aadl.ramses.control.workflow.AbstractLoop ;
+import fr.tpt.aadl.ramses.control.workflow.ResolutionMethod ;
+import fr.tpt.aadl.ramses.control.workflow.WorkflowPilot ;
+import fr.tpt.aadl.ramses.generation.target.specific.AadlTargetSpecificGenerator ;
+import fr.tpt.aadl.ramses.generation.target.specific.LoopManager ;
+import fr.tpt.aadl.ramses.transformation.launcher.ArchitectureRefinementProcessLauncher ;
+import fr.tpt.aadl.ramses.transformation.selection.ITransformationSelection ;
+import fr.tpt.aadl.ramses.transformation.selection.RuleApplicationUtils ;
+import fr.tpt.aadl.ramses.transformation.selection.TransformationRuleAlternative ;
+import fr.tpt.aadl.ramses.transformation.selection.dependency.graph.graph.DependencyGraph ;
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/mcda/TransformationRuleSelection.java

@@ -1,0 +1,58 @@
+package fr.tpt.aadl.ramses.transformation.selection.mcda;
+
+import java.util.ArrayList ;
+import java.util.List ;
+import java.util.Map ;
+
+import org.eclipse.emf.ecore.EObject ;
+
+import fr.tpt.aadl.ramses.transformation.trc.TrcSpecification ;
+import fr.tpt.aadl.ramses.transformation.trc.util.RuleApplicationTulpe ;
+
+public class TransformationRuleSelection
+{
+
+  private TrcSpecification trc;
+  private Map<List<EObject>, ArrayList<String>> alternativeMap;
+  
+  public TransformationRuleSelection(TrcSpecification trc, 
+                                     Map<List<EObject>, ArrayList<String>> alternativeMap)
+  {
+    this.trc = trc;
+    this.alternativeMap = alternativeMap;
+  }
+
+  public List<RuleApplicationTulpe> selectBestRulesAlternatives()
+  {
+    // 1 - order potential results
+    List<List<RuleApplicationTulpe>> orderedPotentialResults =
+      orderPotentialSolutions();
+    
+    
+    
+    for(List<RuleApplicationTulpe> potentialResults
+        : orderedPotentialResults)
+    {
+      // 2 - validate dependencies
+      DependencyValidation depValidation = 
+          new DependencyValidation(trc,potentialResults);
+      
+      boolean validResult = depValidation.validate();
+      if(validResult)
+        return potentialResults;
+    }
+    return null ;
+  }
+
+  private List<List<RuleApplicationTulpe>> orderPotentialSolutions()
+  {
+    // TODO Auto-generated method stub
+    // SG, if you can work on that part, it would be great
+    // attribute trc would give you the impact of transformations on QA
+    // attribute alternativeMap gives you the transformation rules alternatives to consider
+    
+    return null ;
+  }
+  
+  
+}

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection.sensitivity/src/fr/tpt/aadl/ramses/transformation/selection/sensitivity/SensitivityBasedSelection.java

@@ -37,6 +37,7 @@ import fr.tpt.aadl.ramses.generation.target.specific.LoopManager ;
 import fr.tpt.aadl.ramses.transformation.launcher.ArchitectureRefinementProcessLauncher ;
 import fr.tpt.aadl.ramses.transformation.selection.ITransformationSelection ;
 import fr.tpt.aadl.ramses.transformation.selection.RuleApplicationUtils ;
+import fr.tpt.aadl.ramses.transformation.selection.TransformationRuleAlternative ;
 import fr.tpt.aadl.ramses.transformation.selection.TupleEntry ;
 import fr.tpt.aadl.ramses.transformation.selection.utils.SelectionAlgorithm ;
 import fr.tpt.aadl.ramses.transformation.tip.ElementTransformation ;
@@ -379,7 +380,9 @@ public class SensitivityBasedSelection implements ITransformationSelection,LoopM
 			// so options have to be considered in lists of combinations, and the choice
 			// (selectBestTransformation) is made with 
 			// execute the selection algorithm for dependencies
-			RuleApplicationUtils.setTransformationToApply(tuple, transformationsToApply.get(0), tuplesToApply);
+			TransformationRuleAlternative tra = new TransformationRuleAlternative(tuple.getKey(), 
+                                                                            tuple.getValue());
+			RuleApplicationUtils.setTransformationToApply(tra, transformationsToApply.get(0), tuplesToApply);
 			
 			treatedObjects.add(tuple.getKey());
 			List<RuleApplicationTulpe> ruleApplicationList = selectBestTransformation(inclusionDependencies, new ArrayList<String>());
@@ -395,7 +398,10 @@ public class SensitivityBasedSelection implements ITransformationSelection,LoopM
 							&& newTuple.getValue().contains(rat.getTransformationRuleName())
 					  )
 					{
-						RuleApplicationUtils.setTransformationToApply(newTuple, rat.getTransformationRuleName(), tuplesToApply);
+					  TransformationRuleAlternative newTra = new TransformationRuleAlternative(newTuple.getKey(), 
+					                                                                        newTuple.getValue());
+			      
+						RuleApplicationUtils.setTransformationToApply(newTra, rat.getTransformationRuleName(), tuplesToApply);
 						treatedObjects.add(newTuple.getKey());
 					}
 				}
@@ -423,7 +429,10 @@ public class SensitivityBasedSelection implements ITransformationSelection,LoopM
 		  {
[…]

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.selection/src/fr/tpt/aadl/ramses/transformation/selection/RuleApplicationUtils.java

@@ -19,14 +19,14 @@ public class RuleApplicationUtils {
 		return rulesInheritenceMap;
 	}
 	
-	public static void setTransformationToApply(Entry<List<EObject>, ArrayList<String>> tupleWithAlternatives, 
+	public static void setTransformationToApply(TransformationRuleAlternative tupleWithAlternatives, 
 			String transformationToApply,
 			ArrayList<ElementTransformation> tuplesToApply)
 	{
-		ElementTransformation et = TipUtils.createElementTransformation((List<EObject>) tupleWithAlternatives.getKey(), transformationToApply);
+		ElementTransformation et = TipUtils.createElementTransformation((List<EObject>) tupleWithAlternatives.getMatchedElements(), transformationToApply);
 		tuplesToApply.add(et);
 		// Exclude not selected rules
-		for(String s: tupleWithAlternatives.getValue())
+		for(String s: tupleWithAlternatives.getAlternativeRules())
 		{
 			List<String> toExclude = new ArrayList<String>();
 			if(s.equals(transformationToApply))
@@ -52,7 +52,7 @@ public class RuleApplicationUtils {
 			}
 			for(String toExcludeRule: toExclude)
 			{
-			  ElementTransformation exc = TipUtils.createElementTransformation((List<EObject>) tupleWithAlternatives.getKey(), toExcludeRule);
+			  ElementTransformation exc = TipUtils.createElementTransformation((List<EObject>) tupleWithAlternatives.getMatchedElements(), toExcludeRule);
 			  exc.setIsExclusion(true);
 			  tuplesToApply.add(exc);
 			}

### 2014-11-06 model2model/fr.tpt.aadl.ramses.transformation.trc/src/fr/tpt/aadl/ramses/transformation/trc/util/TaggedRuleApplicationTulpe.java

@@ -1,9 +1,5 @@
 package fr.tpt.aadl.ramses.transformation.trc.util;
 
-import java.util.List;
-
-import org.eclipse.emf.ecore.EObject;
-
 public class TaggedRuleApplicationTulpe extends RuleApplicationTulpe {
 
 	boolean _exclusion=false;

### 2014-11-07 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/mcda/MCDABasedTransformationSelection.java
add indications for SG's implementation

@@ -90,6 +90,7 @@ public class MCDABasedTransformationSelection implements ITransformationSelectio
     
     ResourceSet rs = currentImplResource.getResourceSet();
     
+    
     String trcPath = prop.getProperty("ArchitectureRefinementLauncher.trc");
     if(trcPath!=null)
       TrcParser.parse(trcPath, rs);
@@ -152,8 +153,12 @@ public class MCDABasedTransformationSelection implements ITransformationSelectio
         }
         
         // 4 - select alternatives for elements in connectedDepGraph
+        SystemInstance sinst = (SystemInstance) this.currentImplResource.getContents().get(0);
         TransformationRuleSelection trs = 
-            new TransformationRuleSelection(trc, connectedAlternativesMap);
+            new TransformationRuleSelection(trc, 
+                                            sinst,
+                                            connectedAlternativesMap);
+        
         List<RuleApplicationTulpe> ratList = trs.selectBestRulesAlternatives();
         
         for(RuleApplicationTulpe rat:ratList)

### 2014-11-07 model2model/fr.tpt.aadl.ramses.transformation.selection.mcda/src/fr/tpt/aadl/ramses/transformation/selection/mcda/TransformationRuleSelection.java

@@ -5,6 +5,7 @@ import java.util.List ;
 import java.util.Map ;
 
 import org.eclipse.emf.ecore.EObject ;
+import org.osate.aadl2.instance.SystemInstance ;
 
 import fr.tpt.aadl.ramses.transformation.trc.TrcSpecification ;
 import fr.tpt.aadl.ramses.transformation.trc.util.RuleApplicationTulpe ;
@@ -14,12 +15,15 @@ public class TransformationRuleSelection
 
   private TrcSpecification trc;
   private Map<List<EObject>, ArrayList<String>> alternativeMap;
+  private SystemInstance rootSystem;
   
-  public TransformationRuleSelection(TrcSpecification trc, 
+  public TransformationRuleSelection(TrcSpecification trc,
+                                     SystemInstance rootSystem,
                                      Map<List<EObject>, ArrayList<String>> alternativeMap)
   {
     this.trc = trc;
     this.alternativeMap = alternativeMap;
+    this.rootSystem = rootSystem;
   }
 
   public List<RuleApplicationTulpe> selectBestRulesAlternatives()
@@ -46,10 +50,19 @@ public class TransformationRuleSelection
 
   private List<List<RuleApplicationTulpe>> orderPotentialSolutions()
   {
-    // TODO Auto-generated method stub
-    // SG, if you can work on that part, it would be great
-    // attribute trc would give you the impact of transformations on QA
-    // attribute alternativeMap gives you the transformation rules alternatives to consider
+
+    // TODO: SG, if you can work on that part, it would be great
+    // attribute "trc" would give you the impact of transformations on QA
+    // attribute "alternativeMap" gives you the transformation rules alternatives to consider
+    // QA model (quality attibutes definition and weights) is an excel file referenced
+    // air files should be obtained from EObjects in the matched elements
+    //    --> compute average values if several (and different) air files are referenced
+    
+    // from the root system
+    List<List<RuleApplicationTulpe>> result = 
+        new ArrayList<List<RuleApplicationTulpe>>();
+    // 1 - browse elements in alternativeMap to construct "result" 
+     
     
     return null ;
   }
